---
title: "Exploring vital rate models"
author: "Kelley Erickson"
date: "May 16, 2019"
output: html_document
---
<style type="text/css">
.table {

    width: 40%;

}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)



```
# 0. Setup
### Load the data 
```{r, load data, message=FALSE}
#Load demographic data
demog<-read.csv("demography_15_clean.csv", head=T)
library(AICcmodavg)
library(fields)
library(viridis)
library(scales)
my.palette <- viridis(9)
```

This is a csv file where each row is a an individual.

The column names are : 

 * `Obs` : Observation number (each plant should have a different observation number; these were assigned post data entry when we discovered that some of the numbers for individuals were reused between sites
 
 * `Site`: Which site (Big Cypress, Cape Canaveral, Chekika, Forty Pierce, Punta Gorda, Wild Turkey)
 
 * `Plant ID`: The tag number of an individual (each individual in a site has a different number, but numbers were reused across sites)
 
 * `Location`: SeedlingPlot (individual located in a seedling plot) or NA (individual not in seedling plot)
 
 * `Date_i`: The date the census took place for censuses i = 1:7
 * `Status_i`: One of four categories for censuses i=1:7:
    * **alive**: individual was alive when censused
    * **firstdead**: the individual was recorded as dead at this census and was alive at the                      last census 
    * **missing**: the individual was not located at this census
    * **prestudy**: the individual had not been tagged yet 
    * **stilldead**: the individual was already marked dead at a previous census
  * `Death_Cause_i`: One of three categories for censuses i = 1:7:
    * **NA**: for individuals that died, there was no reason to suspect their deaths were due               to management actions
    * **sprayed**: individual death attributed to being sprayed with herbicide (these                       individuals should be excluded)
    * **fire**: individual death attributed to fire (these individuals should be excluded                  from analysis)
 * `Rep_stat_i`: One of 4 categories for censuses  i = 1:7:
    * **NA**: for individuals whose reproductive status is unknown at census i 
    * **female**: for individuals who have produced fruit at any previous census up to an                  including census i 
    * **male**: for individuals who have not produced fruit at any previous census (may have               observed male flowers)
    * **pre-reproductive**: for individuals who have not produced fruit at any previous                   census 
  * `Diam_i`: Diameter (in mm) of individual at census i 
  * `Height_i`: Height (in cm) of individual at census i 
  * `Max_i`: Maximum canopy width in cm of individual at census i 
  * `Min_i`: Minimum canopy width in cm of individual at census i 
  * `Multistem`: For each individual takes on one of two values: 
    * **NA**: individuals that are not multistem
    * **FLAG**: Individuals that are multistem
    
## Stack data 
```{r stack data}
#### Restructure the data in a few different ways: 


Dates <- c(rep(2009, 1512), rep(2010, 1512), rep(2011, 1512), rep(2012, 1512), rep(2013, 1512), rep(2014, 1512))



Death_Cause<-c(demog$Death_Cause_2, demog$Death_Cause_3, demog$Death_Cause_4, demog$Death_Cause_5, demog$Death_Cause_6, demog$Death_Cause_7)

Status<-c(demog$Status_1, demog$Status_2, demog$Status_3, demog$Status_4, demog$Status_5, demog$Status_6, demog$Status_7)

Diams<-cbind(demog$Diam_1, demog$Diam_2, demog$Diam_3, demog$Diam_4, demog$Diam_5, demog$Diam_6, demog$Diam_7) 

row.names(Diams)<-demog$Plant_ID

Heights<-cbind(demog$Height_1, demog$Height_2, demog$Height_3, demog$Height_4, demog$Height_5, demog$Height_6, demog$Height_7)

row.names(Heights)<-demog$Plant_ID

Mins<-cbind(demog$Min_1, demog$Min_2, demog$Min_3, demog$Min_4, demog$Min_5, demog$Min_6, demog$Min_7)

row.names(Mins)<-demog$Plant_ID

Maxs<-cbind(demog$Max_1, demog$Max_2, demog$Max_3, demog$Max_4, demog$Max_5, demog$Max_6, demog$Max_7)

row.names(Maxs)<-demog$Plant_ID

Diams_pooled<-rbind( cbind(Diams[,1], Diams[,2]), cbind(Diams[,2], Diams[,3]), cbind(Diams[, 3], Diams[,4]), cbind(Diams[,4], Diams[,5]), cbind(Diams[,5], Diams[,6]), cbind(Diams[, 6], Diams[, 7]))

Diams_pooled<-data.frame(Diams_pooled[,1], Diams_pooled[,2])

names(Diams_pooled)<-c("t", "t_plus_one")

Sites_pooled<-rep(demog$Site, 6)

ID_pooled<-rep(demog$Plant_ID, 6)

Location<-rep(demog$Location, 6)

Genetic_type_pooled<-rep(0, length(Sites_pooled))

#code which sites are which biotype
for (i in 1:length(Genetic_type_pooled)) { 
	if (Sites_pooled[i]=="Big Cypress") Genetic_type_pooled[i]<-"hybrid"
	else if (Sites_pooled[i]=="Cape Canaveral") Genetic_type_pooled[i]<-"hybrid"
	else if (Sites_pooled[i]=="Chekika") Genetic_type_pooled[i]<-"eastern"
	else if (Sites_pooled[i]=="Fort Pierce") Genetic_type_pooled[i]<-"eastern"
	else if (Sites_pooled[i]=="Punta Gorda") Genetic_type_pooled[i]<-"western"
	else Genetic_type_pooled[i]<-"western"
	
}



Heights_pooled<-rbind( cbind(Heights[,1], Heights[,2]), cbind(Heights[,2], Heights[,3]), cbind(Heights[, 3], Heights[,4]), cbind(Heights[,4], Heights[,5]), cbind(Heights[,5], Heights[,6]), cbind(Heights[, 6], Heights[, 7]))

Heights_pooled<-data.frame(Heights_pooled[,1], Heights_pooled[,2])
names(Heights_pooled)<-c("t", "t_plus_one")



#Finish for maxs and mins 

Maxs_pooled<-rbind(cbind(Maxs[,1], Maxs[,2]), cbind(Maxs[,2], Maxs[,3]), 
	cbind(Maxs[,3], Maxs[,4]), cbind(Maxs[,4], Maxs[,5]), 
	cbind(Maxs[,5], Maxs[,6]), cbind(Maxs[,6], Maxs[,7]))
	
Maxs_pooled<-data.frame(Maxs_pooled[,1], Maxs_pooled[,2])
names(Maxs_pooled)<-c("t", "t_plus_one")



Mins_pooled<-rbind( cbind(Mins[,1], Mins[,2]), cbind(Mins[,2], Mins[,3]), 
	cbind(Mins[,3], Mins[,4]), cbind(Mins[,4], Mins[,5]), 
	cbind(Mins[, 5], Mins[,6]), cbind(Mins[,6], Mins[,7]))
	
Mins_pooled<-data.frame(Mins_pooled[,1], Mins_pooled[,2])
names(Mins_pooled)<-c("t", "t_plus_one")




###Use status matrix to get survival matrix
statmat<-as.matrix(demog[, c(6, 14, 22, 30, 38, 46, 54)])
survmat<-statmat
survmat<- ifelse(survmat=="prestudy"|survmat=="missing"|survmat=="still_dead", NA, survmat)
survmat<- ifelse(survmat =="tagged"|survmat=="alive", 1, 0)

survmat_pooled<-rbind( cbind(survmat[,1], survmat[,2]), cbind(survmat[,2], survmat[,3]), cbind(survmat[, 3], survmat[,4]), cbind(survmat[,4], survmat[,5]), cbind(survmat[,5], survmat[,6]), cbind(survmat[, 6], survmat[, 7]))
names(survmat_pooled)<-c("surv_t", "surv_t_plus_one")


survmat_pooled_bysize<-cbind(Diams_pooled[, 1], survmat_pooled[,2])
names(survmat_pooled_bysize)<-c("size_t", "surv_t_plus_one")



#Use reproduction status matrix to get reproduction matrix
repstatmat<-as.matrix(demog[, c(8, 16, 24, 32, 40, 48, 56)])
repmat<-repstatmat
repmat<- ifelse(repmat =="female", 1, 0)
repmat_pooled<-rbind( cbind(repmat[,1], repmat[,2]), cbind(repmat[,2], repmat[,3]), cbind(repmat[, 3], repmat[,4]), cbind(repmat[,4], repmat[,5]), cbind(repmat[,5], repmat[,6]), cbind(repmat[, 6], repmat[, 7]))


pooled<-cbind(ID_pooled, Sites_pooled, Location, Death_Cause, Genetic_type_pooled, Mins_pooled, Maxs_pooled, Diams_pooled, Heights_pooled, repmat_pooled, survmat_pooled, Dates)
names(pooled)<-c("ID", "Site","Location", "Death_Cause", "Genetic_type", "Min_t", "Min_tplus1", "Max_t", "Max_tplus1", "Diameter_t", "Diameter_tplus1", "Height_t", "Height_tplus1", "Rep_t", "Rep_tplus1", "Surv_t", "Surv_tplus1", "Year")
```

## Investigate relationships among possible state variables 
```{r, investigate state variables}
predictors<-cbind(pooled$Min_t, pooled$Diameter_t, pooled$Height_t, pooled$Max_t)

# What is the correlation amongst the predictor variables? 
correlation<-cor(predictors[, 1:4], use="pairwise.complete.obs")
colnames(correlation)<-c("Min", "Diameter", "Height", "Max")
rownames(correlation)<-c("Min", "Diameter", "Height", "Max")

correlation<-round(correlation, 2)
print(correlation)
#Over the entire dataset, there is the lowest correlation between diameter and height

```

## Exclude outliers 

```{r, exclude outliers}
#Remove individual deaths that were sprayed or fire or grinding
restrict<-subset(pooled, is.na(Death_Cause))

#Remove outliers (very large diameters)
restrict2<-subset(restrict, Diameter_t<800)

#Questioning why we did this? does this lead to model-eviction? 
#Range of diameter: [0, 800]
0.9*max(restrict2$Diameter_t) #700
#Range of height:  [0, 800]
0.9*max(restrict2$Height_t, na.rm=T) #800
```

## Divide dataset into size domains (seedlings and larges)
```{r divide data}
seedlings<-subset(restrict2, restrict2$Diameter_t<1.6)
seedlings<-subset(seedlings, seedlings$Height_t<16)
larges<-subset(restrict2, restrict2$Diameter_t>1.6)
larges<-subset(larges, larges$Height_t>16)

x1seq_larges<-seq(1.6, 800, length.out=50)
x2seq_larges<-seq(16, 800, length.out=50)

x1seq_seedlings<-seq(0, 1.6, length.out=50)
x2seq_seedlings<-seq(0, 16, length.out=50)

```
# Exploratory Statistics 
There are 1512 individuals 

Big Cypress | Cape Canaveral | Chekika | Fort Pierce | Punta Gorda | Wild Turkey
------------|----------------|---------|-------------|-------------|------------
308         | 226            | 460     | 166         | 175         | 177        

Eastern | Hybrid | Western 
--------|--------|--------
  626   | 534    | 352
  
```{r exploratory statistics}
summary(seedlings$Site)
summary(seedlings$Genetic_type)
summary(as.factor(seedlings$Year))
        
summary(larges$Site)
summary(larges$Genetic_type)
summary(as.factor(larges$Year))

```
The number of deaths (0) by biotype:
```{r deaths by biotype}
table(seedlings$Surv_tplus1, seedlings$Genetic_type)
table(larges$Surv_tplus1, larges$Genetic_type)
```
The number of deaths(0) by site:
```{r deaths by site}
table(seedlings$Surv_tplus1, seedlings$Site)
table(larges$Surv_tplus1, larges$Site)

```
```{r deaths by year}
table(seedlings$Surv_tplus1, seedlings$Year)
table(larges$Surv_tplus1, larges$Year)

```
# Define some plotting variables: 

```{r setup plotting}
x1seq_seedlings<-seq(0, 1.6, length.out=50)

x2seq_seedlings<-seq(0, 16, length.out=50)
x1seq_larges <- seq(0, 800, length.out = 50 )
x2seq_larges <- seq (0, 800, length.out = 50)

invlogit<-function(x){exp(x)/(1+exp(x))}

# Function to do an image plot of a matrix in the usual orientation, A(1,1) at top left  
matrix.image=function(x,y,A,col=topo.colors(200),...) {
	nx=length(x); ny=length(y); 
	x1=c(1.5*x[1]-0.5*x[2],1.5*x[nx]-0.5*x[nx-1]); 
	y1=c(1.5*y[1]-0.5*y[2],1.5*y[ny]-0.5*y[ny-1]); 
	image.plot(list(x=x,y=y,z=t(A)),xlim=x1,ylim=rev(y1),col=col,bty="u",...);  
}

```
# 2. Adult Survival models 
Choosing which state variables to use and whether to include terms for biotype, site or year
(for the year effect, only including data from years where all sites were sampled, so AIC cannot be compared with other models) 

* Diameter-only models: 
    * s1: logit(S2) = b0 + b1(diameter)
    * s2: logit(S2) = b0 + b1(diameter) + epsilon(biotype{E,H,W})
    * s3: logit(S2) = b0 + b1(diameter) + epsilon(site{BC, CC, C, FP, PG, WT})
    * s4: logit(S2) = b0 + b1(diameter) + epsilon(year{2010, 2011, 2012, 2013, 2014}
* Height-only models
    * s5: logit(S2) = b0 + b1(height)
    * s6: logit(S2) = b0 + b1(height) + epsilon(biotype{E,H,W})
    * s7: logit(S2) = b0 + b1(height) + epsilon(site{BC, CC, C, FP, PG, WT})
    * s8: logit(S2) = b0 + b1(height) + epsilon(year{2010, 2011, 2012, 2013, 2014}
* Diameter + Height models
    * s9: logit(S2) = b0 + b1(diameter) + b2(height)
    * s10: logit(S2) = b0 + b1(diameter) + b2(height) + epsilon(biotype{E,H,W})
    * s11: logit(S2) = b0 + b1(diameter) + b2(height) + epsilon(site{BC, CC, C, FP, PG,WT})
    * s12: loigt(S2) = b0 + b1(diameter) + b2(height) + epsilon(year{2010, 2011, 2012, 2013, 2014})

### -Diameter-only models

### -- s2_1: logit(S2) = b0 + b1(diameter) -----
```{r s2_1}

  s2_1 <- glm(larges$Surv_tplus1 ~ larges$Diameter_t, family = binomial)
  summary(s2_1)

plot(x1seq_larges, invlogit(s2_1$coeff[1] + s2_1$coeff[2]*x1seq_larges), type='l', ylim=c(0,1) , xlab = "Diameter (t)", ylab="P(Survival)")
points(larges$Diameter_t, larges$Surv_tplus1)


```

### --s2_2: logit(S2) = b0 + b1(diameter) + epsilon(biotype{E,H,W})
Western is not significantly different from Eastern
```{r s2_2, fig.width=9, fig.height=4}
s2_2 <- glm(larges$Surv_tplus1 ~ larges$Diameter_t + larges$Genetic_type, family = binomial)
summary(s2_2)

par(mfrow=c(1, 2))

plot(x1seq_larges, invlogit(s2_2$coeff[1] + s2_2$coeff[2]*x1seq_larges), type='l', ylim=c(0,1) , xlab = "Diameter (t)", ylab="P(Survival)", main = "Eastern, Western")
points(larges[larges$Genetic_type=="eastern" | larges$Genetic_type == "western", ]$Diameter_t, larges[larges$Genetic_type=="eastern" | larges$Genetic_type == "western", ]$Surv_tplus1)

plot(x1seq_larges, invlogit(s2_2$coeff[1] + s2_2$coeff[2]*x1seq_larges + s2_2$coeff[3]), type='l', ylim=c(0,1) , xlab = "Diameter (mm)", ylab="P(Survival)", main = "Hybrid")
points(larges[larges$Genetic_type=="hybrid", ]$Diameter_t, larges[larges$Genetic_type=="hybrid", ]$Surv_tplus1)


 
```

### --s2_3: logit(S2) = b0 + b1(diameter) + epsilon(biotype{BC, CC, C, FP, PG, WT})

Big Cypress, Cape Canaveral, and Punta Gorda are not different  
```{r s2_3}
  s2_3 <- glm(larges$Surv_tplus1 ~ larges$Diameter_t + larges$Site, family = 
              binomial)
  summary(s2_3)
  
  par(mfrow=c(2, 2))

plot(x1seq_larges, invlogit(s2_3$coeff[1] + s2_3$coeff[2]*x1seq_larges), type='l', ylim=c(0,1) , xlab = "Diameter (mm)", ylab="P(Survival)", main = "BC, CC, PG")
points(larges[larges$Site=="Big Cypress" | larges$Site == "Punta Gorda" | larges$Site == "Cape Canaveral", ]$Diameter_t, larges[larges$Site=="Big Cypress" | larges$Site == "Punta Gorda" | larges$Site == "Cape Canaveral", ]$Surv_tplus1)

plot(x1seq_larges, invlogit(s2_3$coeff[1] + s2_3$coeff[2]*x1seq_larges + s2_3$coeff[4]), type='l', ylim=c(0,1) , xlab = "Diameter (mm)", ylab="P(Survival)", main = "C")
points(larges[larges$Site=="Chekika" , ]$Diameter_t, larges[larges$Site=="Chekika", ]$Surv_tplus1)

plot(x1seq_larges, invlogit(s2_3$coeff[1] + s2_3$coeff[2]*x1seq_larges + s2_3$coeff[5]), type='l', ylim=c(0,1) , xlab = "Diameter (mm)", ylab="P(Survival)", main = "FP")
points(larges[larges$Site=="Fort Pierce" , ]$Diameter_t, larges[larges$Site=="Fort Pierce", ]$Surv_tplus1)

plot(x1seq_larges, invlogit(s2_3$coeff[1] + s2_3$coeff[2]*x1seq_larges + s2_3$coeff[7]), type='l', ylim=c(0,1) , xlab = "Diameter (mm)", ylab="P(Survival)", main = "WT")
points(larges[larges$Site=="Wild Turkey" , ]$Diameter_t, larges[larges$Site=="Wild Turkey", ]$Surv_tplus1)


```


### --s2_4: logit(S2) = b0 + b1(diameter) + epsilon(year{2010, 2011, 2012, 2013}
```{r s2_4} 
larges2 <- subset(larges, larges$Year > 2009 & larges$Year <2014)
larges2$Year <- as.factor(larges2$Year)
s2_4 <- glm(larges2$Surv_tplus1 ~ larges2$Diameter_t + larges2$Year, family = binomial)
summary(s2_4)


par(mfrow=c(2,2))
plot(x1seq_larges, invlogit(s2_4$coeff[1] + s2_4$coeff[2]*x1seq_larges ), type='l', ylim=c(0,1) , xlab = "Diameter (mm)", ylab="P(Survival)", main = "2010")
points(larges2[larges2$Year=="2010", ]$Diameter_t, larges2[larges2$Year=="2010", ]$Surv_tplus1)
plot(x1seq_larges, invlogit(s2_4$coeff[1] + s2_4$coeff[2]*x1seq_larges + s2_4$coeff[3] ), type='l', ylim=c(0,1) , xlab = "Diameter (mm)", ylab="P(Survival)", main = "2011")
points(larges2[larges2$Year=="2011", ]$Diameter_t, larges2[larges2$Year=="2011", ]$Surv_tplus1)
plot(x1seq_larges, invlogit(s2_4$coeff[1] + s2_4$coeff[2]*x1seq_seedlings + s2_4$coeff[4] ), type='l', ylim=c(0,1) , xlab = "Diameter (mm)", ylab="P(Survival)", main = "2012")
points(larges2[larges2$Year=="2012", ]$Diameter_t, larges2[larges2$Year=="2012", ]$Surv_tplus1)

plot(x1seq_larges, invlogit(s2_4$coeff[1] + s2_4$coeff[2]*x1seq_larges + s2_4$coeff[5] ), type='l', ylim=c(0,1) , xlab = "Diameter (mm)", ylab="P(Survival)", main = "2013")
points(larges2[larges2$Year=="2013", ]$Diameter_t, larges2[larges2$Year=="2013", ]$Surv_tplus1)

```

### - Height-only models 
### --s2_5: logit(S2) = b0 + b1(height) 
```{r s2_5}
  s2_5 <- glm(larges$Surv_tplus1 ~ larges$Height_t, family = binomial)
  summary(s2_5)

plot(x2seq_larges, invlogit(s2_5$coeff[1] + s2_5$coeff[2]*x2seq_larges), type='l', ylim=c(0,1) , xlab = "Height (cm)", ylab="P(Survival)")
points(larges$Height_t, larges$Surv_tplus1)

```
### --s2_6: logit(S2) = b0 + b1(height) + epsilon(biotype{E,H,W})
Eastern and Western are not significantly different. 
```{r s2_6}
 s2_6 <- glm(larges$Surv_tplus1 ~ larges$Height_t + larges$Genetic_type, family = binomial) 
summary(s2_6)

par(mfrow=c(1, 2))

plot(x2seq_larges, invlogit(s2_6$coeff[1] + s2_6$coeff[2]*x2seq_larges), type='l', ylim=c(0,1) , xlab = "Height(cm)", ylab="P(Survival)", main = "Eastern, Western")
points(larges[larges$Genetic_type=="eastern" | larges$Genetic_type == "western", ]$Height_t, seedlings[larges$Genetic_type=="eastern" | larges$Genetic_type == "western", ]$Surv_tplus1)

plot(x2seq_larges, invlogit(s2_6$coeff[1] + s2_6$coeff[2]*x2seq_larges + s2_6$coeff[3]), type='l', ylim=c(0,1) , xlab = "Height(cm)", ylab="P(Survival)", main = "Hybrid")
points(larges[larges$Genetic_type=="hybrid", ]$Height_t, seedlings[larges$Genetic_type=="hybrid", ]$Surv_tplus1)


```
### --s2_7: logit(S2) = b0 + b1(height) + epsilon(site{BC, CC, C, FP, PG, WT})
Big Cypress, Chekika, Punta Gorda and Wild Turkey are not significantly different 
```{r s7} 
  s2_7 <- glm(larges$Surv_tplus1 ~ larges$Height_t + larges$Site, family = binomial)
  summary(s2_7)
  
  par(mfrow=c(1,3))
  plot(x2seq_larges, invlogit(s2_7$coeff[1] + s2_7$coeff[2]*x2seq_larges), type='l', ylim=c(0,1) , xlab = "Height(cm)", ylab="P(Survival)", main = "Remaining sites")
points(larges[larges$Site!= "Chekika" & larges$Site!="Wild Turkey", ]$Height_t, larges[larges$Site!= "Chekika" & larges$Site!="Wild Turkey", ]$Surv_tplus1)

  plot(x2seq_larges, invlogit(s2_7$coeff[1] + s2_7$coeff[2]*x2seq_larges + s2_7$coeff[4]), type='l', ylim=c(0,1) , xlab = "Height(cm)", ylab="P(Survival)", main = "C")
points(larges[larges$Site== "Chekika", ]$Height_t, larges[larges$Site== "Chekika", ]$Surv_tplus1)

  plot(x2seq_larges, invlogit(s2_7$coeff[1] + s2_7$coeff[2]*x2seq_larges + s2_7$coeff[7]), type='l', ylim=c(0,1) , xlab = "Height(cm)", ylab="P(Survival)", main = "WT")
points(larges[larges$Site== "Wild Turkey", ]$Height_t, larges[larges$Site== "Wild Turkey", ]$Surv_tplus1)




  
```
### --s2_8: logit(S2) = b0 + b1(height) + epsilon(year{2010, 2011, 2012, 2013}
2010 and 2011 are not different 
```{r s8}
s2_8 <- glm(larges2$Surv_tplus1 ~ larges2$Height_t + larges2$Year, family = binomial)
summary(s2_8)


par(mfrow=c(2,2))
plot(x1seq_larges, invlogit(s2_8$coeff[1] + s2_8$coeff[2]*x2seq_larges ), type='l', ylim=c(0,1) , xlab = "Height(cm)", ylab="P(Survival)", main = "2010-2011, 2011-2012")
points(larges2[larges2$Year=="2010" | larges2$Year == "2011", ]$Diameter_t, larges2[larges2$Year=="2010" | larges2$Year == "2011", ]$Surv_tplus1)

plot(x1seq_larges, invlogit(s2_8$coeff[1] + s2_8$coeff[2]*x2seq_larges + s2_8$coeff[4]), type='l', ylim=c(0,1) , xlab = "Height(cm)", ylab="P(Survival)", main = "2012-2013")
points(larges2[larges2$Year=="2012", ]$Diameter_t, larges2[larges2$Year=="2012", ]$Surv_tplus1)

plot(x1seq_larges, invlogit(s2_8$coeff[1] + s2_8$coeff[2]*x2seq_larges + s2_8$coeff[5]), type='l', ylim=c(0,1) , xlab = "Height(cm)", ylab="P(Survival)", main = "2013-2014")
points(larges2[larges2$Year=="2013", ]$Diameter_t, larges2[larges2$Year=="2013", ]$Surv_tplus1)







```
### - Diameter + Height models 
### --s2_9: logit(S2) = b0 + b1(diameter) + b2(height)
```{r s9}
  s2_9 <- glm(larges$Surv_tplus1 ~ larges$Diameter_t + larges$Height_t, family = 
                binomial)
  summary(s2_9)
  
 b0<- s2_9$coeff[1]
 b1<- s2_9$coeff[2]
 b2<- s2_9$coeff[3]


z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))

pmat<-persp(x1seq_larges, x2seq_larges, z1, ticktype="detailed",
      theta=-30, zlim=c(0, 1.25), zlab="\n P(Survival)", 
      shade=0.1, nticks=4, xlab="\n Diameter (mm)", 
      ylab="\n Height (cm)",  lwd=1, xaxs="i", 
      main="", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(larges$Diameter_t, larges$Height_t, larges$Surv_tplus1, pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)


par(mar=c(5.1,4.1,4.1,6))
image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", col=alpha(my.palette,0.8), legend.lab = "P(Survival)")
points(larges$Diameter_t[larges$Surv_tplus1==1], larges$Height_t[larges$Surv_tplus1==1], pch=19)
points(larges$Diameter_t[larges$Surv_tplus1==0], larges$Height_t[larges$Surv_tplus1==0], pch=1)
image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", col=alpha(my.palette,0.4), legend.lab = "P(Survival)", add = T)
legend(1.63, 15, pch=c(1,19), cex = 0.8, text.width=0.19, c("Died", "Survived"), xpd=T)
```
### --s2_10: logit(S2) = b0 + b1(diameter) + b2(height) + epsilon(biotype{E,H,W})
Eastern and Western are not different 
```{r s2_10}
 s2_10 <- glm(larges$Surv_tplus1~ larges$Diameter_t + larges$Height_t +larges$Genetic_type,         family=binomial)
summary(s2_10)
par(mfrow=c(1,2))

#E/W
b0 <- s2_10$coeff[1]
b1 <- s2_10$coeff[2]
b2 <- s2_10$coeff[3]
z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))

pmat<-persp(x1seq_larges, x2seq_larges, z1, ticktype="detailed",
      theta=-30, zlim=c(0, 1.25), zlab="\n P(Survival)", 
      shade=0.1, nticks=4, xlab="\n Diameter (mm)", 
      ylab="\n Height (cm)",  lwd=1, xaxs="i", 
      main="Eastern, Western", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(larges$Diameter_t[larges$Genetic_type=="eastern" | larges$Genetic_type == "western"], larges$Height_t[larges$Genetic_type=="eastern" | larges$Genetic_type == "western"], larges$Surv_tplus1[larges$Genetic_type=="eastern" | larges$Genetic_type == "western"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)
#H
b0 <- s2_10$coeff[1] + s2_10$coeff[4]
b1 <- s2_10$coeff[2]
b2 <- s2_10$coeff[3]


z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))

pmat<-persp(x1seq_larges, x2seq_larges, z1, ticktype="detailed",
      theta=-30, zlim=c(0, 1.25), zlab="\n P(Survival)", 
      shade=0.1, nticks=4, xlab="\n Diameter (mm)", 
      ylab="\n Height (cm)",  lwd=1, xaxs="i", 
      main="Hybrid", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(larges$Diameter_t[larges$Genetic_type=="hybrid"], larges$Height_t[larges$Genetic_type=="hybrid"], larges$Surv_tplus1[larges$Genetic_type=="hybrid"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col="red")

###### Image plots 
par(mfrow=c(1,2))
par(mar=c(5.1,4.1,4.1,6))
#EASTERN
b0 <- s2_10$coeff[1]
b1 <- s2_10$coeff[2]
b2 <- s2_10$coeff[3]

z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))
image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", col=alpha(my.palette,0.8), legend.lab = "P(Survival)", main = "Eastern, Western")

points(larges$Diameter_t[larges$Surv_tplus1==1 & (larges$Genetic_type == "eastern" | larges$Genetic_type == "western")], larges$Height_t[larges$Surv_tplus1==1 & (larges$Genetic_type == "eastern" | larges$Genetic_type == "western")], pch=19)
points(larges$Diameter_t[larges$Surv_tplus1==0 &(larges$Genetic_type == "eastern" | larges$Genetic_type == "western")], larges$Height_t[larges$Surv_tplus1==0 &(larges$Genetic_type == "eastern" | larges$Genetic_type =="western")], pch=1)
image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", col=alpha(my.palette,0.4), legend.lab = "P(Survival)", add = T)

#Hybrid
b0 <- s2_10$coeff[1] + s2_10$coeff[4]
b1 <- s2_10$coeff[2]
b2 <- s2_10$coeff[3]

z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))
image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", col=alpha(my.palette,0.8), legend.lab = "P(Survival)", main = "Hybrid")
points(larges$Diameter_t[larges$Surv_tplus1==1 & larges$Genetic_type == "hybrid"], larges$Height_t[larges$Surv_tplus1==1 & larges$Genetic_type == "hybrid"], pch=19)
points(larges$Diameter_t[larges$Surv_tplus1==0 &larges$Genetic_type == "hybrid"], larges$Height_t[larges$Surv_tplus1==0 &larges$Genetic_type == "hybrid"], pch=1)
image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", col=alpha(my.palette,0.4), legend.lab = "P(Survival)", add = T)











```
### --s2_11: logit(S2) = b0 + b1(diameter) + b2(height) + epsilon(site{BC, CC, C, FP, PG,WT})

Big Cypress, Cape Canaveral and Punta Gorda are not different 
```{r s2_11}
s2_11 <- glm(larges$Surv_tplus1 ~ larges$Diameter_t + larges$Height_t + 
              larges$Site, family = binomial)
summary(s2_11)
 
par(mfrow=c(2,2)) 
  #Big Cypress, Cape Canaveral and Punta Gorda 
b0 <- s2_11$coeff[1]
b1 <- s2_11$coeff[2]
b2 <- s2_11$coeff[3]
z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))

pmat<-persp(x1seq_larges, x2seq_larges, z1, ticktype="detailed",
      theta=-30, zlim=c(0, 1.25), zlab="\n P(Survival)", 
      shade=0.1, nticks=4, xlab="\n Diameter (mm)", 
      ylab="\n Height (cm)",  lwd=1, xaxs="i", 
      main="BC, CC, PG", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(larges$Diameter_t[larges$Site=="Big Cypress" | larges$Site == "Cape Canaveral" | larges$Site == "Punta Gorda"], larges$Height_t[larges$Site=="Big Cypress" | larges$Site == "Cape Canaveral" | larges$Site == "Punta Gorda"], larges$Surv_tplus1[larges$Site=="Big Cypress" | larges$Site == "Cape Canaveral" | larges$Site == "Punta Gorda"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)

#Chekika
b0 <- s2_11$coeff[1] + s2_11$coeff[5]
b1 <- s2_11$coeff[2] 
b2 <- s2_11$coeff[3]
z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))

pmat<-persp(x1seq_larges, x2seq_larges, z1, ticktype="detailed",
      theta=-30, zlim=c(0, 1.25), zlab="\n P(Survival)", 
      shade=0.1, nticks=4, xlab="\n Diameter (mm)", 
      ylab="\n Height (cm)",  lwd=1, xaxs="i", 
      main="C", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(larges$Diameter_t[larges$Site=="Chekika"], larges$Height_t[larges$Site=="Chekika"], larges$Surv_tplus1[larges$Site=="Chekika"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)


#Fort Pierce
b0 <- s2_11$coeff[1] + s2_11$coeff[6]
b1 <- s2_11$coeff[2] 
b2 <- s2_11$coeff[3]
z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))

pmat<-persp(x1seq_larges, x2seq_larges, z1, ticktype="detailed",
      theta=-30, zlim=c(0, 1.25), zlab="\n P(Survival)", 
      shade=0.1, nticks=4, xlab="\n Diameter (mm)", 
      ylab="\n Height (cm)",  lwd=1, xaxs="i", 
      main="FP", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(larges$Diameter_t[larges$Site=="Chekika"], larges$Height_t[larges$Site=="Chekika"], larges$Surv_tplus1[larges$Site=="Chekika"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)

#Wild Turkey
b0 <- s2_11$coeff[1] + s2_11$coeff[8]
b1 <- s2_11$coeff[2] 
b2 <- s2_11$coeff[3]
z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))

pmat<-persp(x1seq_larges, x2seq_larges, z1, ticktype="detailed",
      theta=-30, zlim=c(0, 1.25), zlab="\n P(Survival)", 
      shade=0.1, nticks=4, xlab="\n Diameter (mm)", 
      ylab="\n Height (cm)",  lwd=1, xaxs="i", 
      main="WT", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(larges$Diameter_t[larges$Site=="Wild Turkey"], larges$Height_t[larges$Site=="Wild Turkey"], larges$Surv_tplus1[larges$Site=="Wild Turkey"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)

####### Image plots

par(mfrow=c(2,2)) 
#Big Cypress, Cape Canaveral and Punta Gorda 
b0 <- s2_11$coeff[1]
b1 <- s2_11$coeff[2]
b2 <- s2_11$coeff[3]
z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))

image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="BC, CC, PG", col=my.palette)
points(larges$Diameter_t[larges$Surv_tplus1==1 & (larges$Site=="Big Cypress" |larges$Site == "Cape Canaveral" | larges$Site == "Punta Gorda")], larges$Height_t[larges$Surv_tplus1==1& (larges$Site=="Big Cypress" |larges$Site == "Cape Canaveral" | larges$Site == "Punta Gorda")], pch=19)
points(larges$Diameter_t[larges$Surv_tplus1==0 & (larges$Site=="Big Cypress" |larges$Site == "Cape Canaveral" | larges$Site == "Punta Gorda")], larges$Height_t[larges$Surv_tplus1==0&(larges$Site=="Big Cypress" |larges$Site == "Cape Canaveral" | larges$Site == "Punta Gorda")], pch=1)
legend("topright", pch=c(1,19), cex = 0.8, c("Died", "Survived"), xpd=T)
image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="BC, CC, PG", col=alpha(my.palette,0.4), add = T)



#Chekika
b0 <- s2_11$coeff[1] + s2_11$coeff[5]
b1 <- s2_11$coeff[2] 
b2 <- s2_11$coeff[3]
z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))

image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="C", col=my.palette)
points(larges$Diameter_t[larges$Surv_tplus1==1 & larges$Site=="Chekika"], larges$Height_t[larges$Surv_tplus1==1& larges$Site=="Chekika"], pch=19)
points(larges$Diameter_t[larges$Surv_tplus1==0 & larges$Site=="Chekika"], larges$Height_t[larges$Surv_tplus1==0&larges$Site=="Chekika"], pch=1)
legend("topright", pch=c(1,19), cex = 0.8, c("Died", "Survived"), xpd=T)
image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="C", col=alpha(my.palette, 0.4), add = T)

#Fort Pierce
b0 <- s2_11$coeff[1] + s2_11$coeff[6]
b1 <- s2_11$coeff[2] 
b2 <- s2_11$coeff[3]
z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))

image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="FP", col=my.palette)
points(larges$Diameter_t[larges$Surv_tplus1==1 & larges$Site=="Fort Pierce"], larges$Height_t[larges$Surv_tplus1==1& larges$Site=="Fort Pierce"], pch=19)
points(larges$Diameter_t[larges$Surv_tplus1==0 & larges$Site=="Fort Pierce"], larges$Height_t[larges$Surv_tplus1==0&larges$Site=="Fort Pierce"], pch=1)
legend("topright", pch=c(1,19), cex = 0.8, c("Died", "Survived"), xpd=T)
image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="FP", col=alpha(my.palette, 0.4), add = T)

#Wild Turkey
b0 <- s2_11$coeff[1] + s2_11$coeff[8]
b1 <- s2_11$coeff[2] 
b2 <- s2_11$coeff[3]
z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))


image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="WT", col=my.palette)
points(larges$Diameter_t[larges$Surv_tplus1==1 & larges$Site=="Wild Turkey"], larges$Height_t[larges$Surv_tplus1==1& larges$Site=="Wild Turkey"], pch=19)
points(larges$Diameter_t[larges$Surv_tplus1==0 & larges$Site=="Wild Turkey"], larges$Height_t[larges$Surv_tplus1==0&larges$Site=="Wild Turkey"], pch=1)
legend("topright", pch=c(1,19), cex = 0.8, c("Died", "Survived"), xpd=T)
image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="WT", col=alpha(my.palette, 0.4), add = T)
```
### --s2_12: logit(S2) = b0 + b1(diameter) + b2(height) + epsilon(year{2010, 2011, 2012, 2013, 2014})
```{r s2_12}
s2_12 <- glm(larges2$Surv_tplus1 ~ larges2$Diameter_t + larges2$Height_t + 
              larges2$Year, family = binomial)
summary(s2_12)
 
par(mfrow=c(2,2)) 
#2010
b0 <- s2_12$coeff[1]
b1 <- s2_12$coeff[2]
b2 <- s2_12$coeff[3]
z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))

pmat<-persp(x1seq_larges, x2seq_larges, z1, ticktype="detailed",
      theta=-30, zlim=c(0, 1.25), zlab="\n P(Survival)", 
      shade=0.1, nticks=4, xlab="\n Diameter (mm)", 
      ylab="\n Height (cm)",  lwd=1, xaxs="i", 
      main="2010", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(larges2$Diameter_t[larges2$Year=="2010"], larges2$Height_t[larges2$Year =="2010"], larges2$Surv_tplus1[larges2$Year=="2010"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)

#2011
b0 <- s2_12$coeff[1] + s2_12$coeff[4]
b1 <- s2_12$coeff[2]
b2 <- s2_12$coeff[3]
z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))

pmat<-persp(x1seq_larges, x2seq_larges, z1, ticktype="detailed",
      theta=-30, zlim=c(0, 1.25), zlab="\n P(Survival)", 
      shade=0.1, nticks=4, xlab="\n Diameter (mm)", 
      ylab="\n Height (cm)",  lwd=1, xaxs="i", 
      main="2011", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(larges2$Diameter_t[larges2$Year=="2011"], larges2$Height_t[larges2$Year =="2011"], seedlings$Surv_tplus1[larges2$Year=="2011"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)


#2012
b0 <- s2_12$coeff[1] + s2_12$coeff[5]
b1 <- s2_12$coeff[2]
b2 <- s2_12$coeff[3]
z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))

pmat<-persp(x1seq_larges, x2seq_larges, z1, ticktype="detailed",
      theta=-30, zlim=c(0, 1.25), zlab="\n P(Survival)", 
      shade=0.1, nticks=4, xlab="\n Diameter (mm)", 
      ylab="\n Height (cm)",  lwd=1, xaxs="i", 
      main="2012", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(larges2$Diameter_t[larges2$Year=="2012"], larges2$Height_t[larges2$Year =="2012"], larges2$Surv_tplus1[larges2$Year=="2012"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)


#2013
b0 <- s2_12$coeff[1] + s2_12$coeff[6]
b1 <- s2_12$coeff[2]
b2 <- s2_12$coeff[3]
z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))

pmat<-persp(x1seq_larges, x2seq_larges, z1, ticktype="detailed",
      theta=-30, zlim=c(0, 1.25), zlab="\n P(Survival)", 
      shade=0.1, nticks=4, xlab="\n Diameter (mm)", 
      ylab="\n Height (cm)",  lwd=1, xaxs="i", 
      main="2013", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(larges2$Diameter_t[larges2$Year=="2013"], larges2$Height_t[larges2$Year =="2013"], larges2$Surv_tplus1[larges2$Year=="2013"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)

####### Image Plots 
par(mfrow=c(2,2))
#2010
b0 <- s2_12$coeff[1] 
b1 <- s2_12$coeff[2] 
b2 <- s2_12$coeff[3]
z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))

image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="2010", col=my.palette)
points(larges2$Diameter_t[larges2$Surv_tplus1==1 & larges2$Year=="2010"], larges2$Height_t[larges2$Surv_tplus1==1& larges2$Year=="2010"], pch=19)
points(larges2$Diameter_t[larges2$Surv_tplus1==0 & larges2$Year=="2010"], larges2$Height_t[larges2$Surv_tplus1==0&larges2$Year=="2010"], pch=1)
legend("topright", pch=c(1,19), cex = 0.8, c("Died", "Survived"), xpd=T)
image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="2010", col=alpha(my.palette, 0.4), add = T)

#2011
b0 <- s2_12$coeff[1] + s2_12$coeff[4]
b1 <- s2_12$coeff[2] 
b2 <- s2_12$coeff[3]
z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))

image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="2011", col=my.palette)
points(larges2$Diameter_t[larges2$Surv_tplus1==1 & larges2$Year=="2011"], larges2$Height_t[larges2$Surv_tplus1==1& larges2$Year=="2011"], pch=19)
points(larges2$Diameter_t[larges2$Surv_tplus1==0 & larges2$Year=="2011"], larges2$Height_t[larges2$Surv_tplus1==0&larges2$Year=="2011"], pch=1)
legend("topright", pch=c(1,19), cex = 0.8, c("Died", "Survived"), xpd=T)
image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="2011", col=alpha(my.palette, 0.4), add = T)

#2012
b0 <- s2_12$coeff[1] +s2_12$coeff[5]
b1 <- s2_12$coeff[2] 
b2 <- s2_12$coeff[3]
z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))

image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="2012", col=my.palette)
points(larges2$Diameter_t[larges2$Surv_tplus1==1 & larges2$Year=="2012"], larges2$Height_t[larges2$Surv_tplus1==1& larges2$Year=="2012"], pch=19)
points(larges2$Diameter_t[larges2$Surv_tplus1==0 & larges2$Year=="2012"], larges2$Height_t[larges2$Surv_tplus1==0&larges2$Year=="2012"], pch=1)
legend("topright", pch=c(1,19), cex = 0.8, c("Died", "Survived"), xpd=T)
image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="2012", col=alpha(my.palette, 0.4), add = T)

#2013
b0 <- s2_12$coeff[1] + s2_12$coeff[6]
b1 <- s2_12$coeff[2] 
b2 <- s2_12$coeff[3]
z1<-outer(x1seq_larges, x2seq_larges, function(a,b) (invlogit(b0 + b1*a + b2*b)))

image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="2013", col=my.palette)
points(larges2$Diameter_t[larges2$Surv_tplus1==1 & larges2$Year=="2013"], larges2$Height_t[larges2$Surv_tplus1==1& larges2$Year=="2013"], pch=19)
points(larges2$Diameter_t[larges2$Surv_tplus1==0 & larges2$Year=="2013"], larges2$Height_t[larges2$Surv_tplus1==0&larges2$Year=="2013"], pch=1)
legend("topright", pch=c(1,19), cex = 0.8, c("Died", "Survived"), xpd=T)
image.plot(x1seq_larges, x2seq_larges, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="2013", col=alpha(my.palette, 0.4), add = T)
```


###- AIC
```{r seedling survival aic}
#For all models except year
aictab(list(s2_1, s2_2, s2_3, s2_5, s2_6, s2_7, s2_9, s2_10, s2_11), modnames= c("s2_1", "s2_2", "s2_3", "s2_5", "s2_6", "s2_7", "s2_9", "s2_10", "s2_11"))

#For comparing among the models with year: 
aictab(list(s2_4, s2_8, s2_12), modnames=c("s2_4", "s2_8", "s2_12"))

```


