---
title: "Exploring vital rate models: D1 Growth"
author: "Kelley Erickson"
date: "May 16, 2019"
output: pdf_document
---
<style type="text/css">
.table {

    width: 40%;

}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)



```
# 0. Setup
### Load the data 
```{r, load data, message=FALSE}
#Load demographic data
demog<-read.csv("demography_15_clean.csv", head=T)
library(AICcmodavg)
library(fields)
library(viridis)
my.palette <- viridis(9)
```

This is a csv file where each row is a an individual.

The column names are : 

 * `Obs` : Observation number (each plant should have a different observation number; these were assigned post data entry when we discovered that some of the numbers for individuals were reused between sites
 
 * `Site`: Which site (Big Cypress, Cape Canaveral, Chekika, Forty Pierce, Punta Gorda, Wild Turkey)
 
 * `Plant ID`: The tag number of an individual (each individual in a site has a different number, but numbers were reused across sites)
 
 * `Location`: SeedlingPlot (individual located in a seedling plot) or NA (individual not in seedling plot)
 
 * `Date_i`: The date the census took place for censuses i = 1:7
 * `Status_i`: One of four categories for censuses i=1:7:
    * **alive**: individual was alive when censused
    * **firstdead**: the individual was recorded as dead at this census and was alive at the                      last census 
    * **missing**: the individual was not located at this census
    * **prestudy**: the individual had not been tagged yet 
    * **stilldead**: the individual was already marked dead at a previous census
  * `Death_Cause_i`: One of three categories for censuses i = 1:7:
    * **NA**: for individuals that died, there was no reason to suspect their deaths were due               to management actions
    * **sprayed**: individual death attributed to being sprayed with herbicide (these                       individuals should be excluded)
    * **fire**: individual death attributed to fire (these individuals should be excluded                  from analysis)
 * `Rep_stat_i`: One of 4 categories for censuses  i = 1:7:
    * **NA**: for individuals whose reproductive status is unknown at census i 
    * **female**: for individuals who have produced fruit at any previous census up to an                  including census i 
    * **male**: for individuals who have not produced fruit at any previous census (may have               observed male flowers)
    * **pre-reproductive**: for individuals who have not produced fruit at any previous                   census 
  * `Diam_i`: Diameter (in mm) of individual at census i 
  * `Height_i`: Height (in cm) of individual at census i 
  * `Max_i`: Maximum canopy width in cm of individual at census i 
  * `Min_i`: Minimum canopy width in cm of individual at census i 
  * `Multistem`: For each individual takes on one of two values: 
    * **NA**: individuals that are not multistem
    * **FLAG**: Individuals that are multistem
    
## Stack data 
```{r stack data}
#### Restructure the data in a few different ways: 


Dates <- c(rep(2009, 1512), rep(2010, 1512), rep(2011, 1512), rep(2012, 1512), rep(2013, 1512), rep(2014, 1512))



Death_Cause<-c(demog$Death_Cause_2, demog$Death_Cause_3, demog$Death_Cause_4, demog$Death_Cause_5, demog$Death_Cause_6, demog$Death_Cause_7)

Status<-c(demog$Status_1, demog$Status_2, demog$Status_3, demog$Status_4, demog$Status_5, demog$Status_6, demog$Status_7)

Diams<-cbind(demog$Diam_1, demog$Diam_2, demog$Diam_3, demog$Diam_4, demog$Diam_5, demog$Diam_6, demog$Diam_7) 

row.names(Diams)<-demog$Plant_ID

Heights<-cbind(demog$Height_1, demog$Height_2, demog$Height_3, demog$Height_4, demog$Height_5, demog$Height_6, demog$Height_7)

row.names(Heights)<-demog$Plant_ID

Mins<-cbind(demog$Min_1, demog$Min_2, demog$Min_3, demog$Min_4, demog$Min_5, demog$Min_6, demog$Min_7)

row.names(Mins)<-demog$Plant_ID

Maxs<-cbind(demog$Max_1, demog$Max_2, demog$Max_3, demog$Max_4, demog$Max_5, demog$Max_6, demog$Max_7)

row.names(Maxs)<-demog$Plant_ID

Diams_pooled<-rbind( cbind(Diams[,1], Diams[,2]), cbind(Diams[,2], Diams[,3]), cbind(Diams[, 3], Diams[,4]), cbind(Diams[,4], Diams[,5]), cbind(Diams[,5], Diams[,6]), cbind(Diams[, 6], Diams[, 7]))

Diams_pooled<-data.frame(Diams_pooled[,1], Diams_pooled[,2])

names(Diams_pooled)<-c("t", "t_plus_one")

Sites_pooled<-rep(demog$Site, 6)

ID_pooled<-rep(demog$Plant_ID, 6)

Location<-rep(demog$Location, 6)

Genetic_type_pooled<-rep(0, length(Sites_pooled))

#code which sites are which biotype
for (i in 1:length(Genetic_type_pooled)) { 
	if (Sites_pooled[i]=="Big Cypress") Genetic_type_pooled[i]<-"hybrid"
	else if (Sites_pooled[i]=="Cape Canaveral") Genetic_type_pooled[i]<-"hybrid"
	else if (Sites_pooled[i]=="Chekika") Genetic_type_pooled[i]<-"eastern"
	else if (Sites_pooled[i]=="Fort Pierce") Genetic_type_pooled[i]<-"eastern"
	else if (Sites_pooled[i]=="Punta Gorda") Genetic_type_pooled[i]<-"western"
	else Genetic_type_pooled[i]<-"western"
	
}



Heights_pooled<-rbind( cbind(Heights[,1], Heights[,2]), cbind(Heights[,2], Heights[,3]), cbind(Heights[, 3], Heights[,4]), cbind(Heights[,4], Heights[,5]), cbind(Heights[,5], Heights[,6]), cbind(Heights[, 6], Heights[, 7]))

Heights_pooled<-data.frame(Heights_pooled[,1], Heights_pooled[,2])
names(Heights_pooled)<-c("t", "t_plus_one")



#Finish for maxs and mins 

Maxs_pooled<-rbind(cbind(Maxs[,1], Maxs[,2]), cbind(Maxs[,2], Maxs[,3]), 
	cbind(Maxs[,3], Maxs[,4]), cbind(Maxs[,4], Maxs[,5]), 
	cbind(Maxs[,5], Maxs[,6]), cbind(Maxs[,6], Maxs[,7]))
	
Maxs_pooled<-data.frame(Maxs_pooled[,1], Maxs_pooled[,2])
names(Maxs_pooled)<-c("t", "t_plus_one")



Mins_pooled<-rbind( cbind(Mins[,1], Mins[,2]), cbind(Mins[,2], Mins[,3]), 
	cbind(Mins[,3], Mins[,4]), cbind(Mins[,4], Mins[,5]), 
	cbind(Mins[, 5], Mins[,6]), cbind(Mins[,6], Mins[,7]))
	
Mins_pooled<-data.frame(Mins_pooled[,1], Mins_pooled[,2])
names(Mins_pooled)<-c("t", "t_plus_one")




###Use status matrix to get survival matrix
statmat<-as.matrix(demog[, c(6, 14, 22, 30, 38, 46, 54)])
survmat<-statmat
survmat<- ifelse(survmat=="prestudy"|survmat=="missing"|survmat=="still_dead", NA, survmat)
survmat<- ifelse(survmat =="tagged"|survmat=="alive", 1, 0)

survmat_pooled<-rbind( cbind(survmat[,1], survmat[,2]), cbind(survmat[,2], survmat[,3]), cbind(survmat[, 3], survmat[,4]), cbind(survmat[,4], survmat[,5]), cbind(survmat[,5], survmat[,6]), cbind(survmat[, 6], survmat[, 7]))
names(survmat_pooled)<-c("surv_t", "surv_t_plus_one")


survmat_pooled_bysize<-cbind(Diams_pooled[, 1], survmat_pooled[,2])
names(survmat_pooled_bysize)<-c("size_t", "surv_t_plus_one")



#Use reproduction status matrix to get reproduction matrix
repstatmat<-as.matrix(demog[, c(8, 16, 24, 32, 40, 48, 56)])
repmat<-repstatmat
repmat<- ifelse(repmat =="female", 1, 0)
repmat_pooled<-rbind( cbind(repmat[,1], repmat[,2]), cbind(repmat[,2], repmat[,3]), cbind(repmat[, 3], repmat[,4]), cbind(repmat[,4], repmat[,5]), cbind(repmat[,5], repmat[,6]), cbind(repmat[, 6], repmat[, 7]))


pooled<-cbind(ID_pooled, Sites_pooled, Location, Death_Cause, Genetic_type_pooled, Mins_pooled, Maxs_pooled, Diams_pooled, Heights_pooled, repmat_pooled, survmat_pooled, Dates)
names(pooled)<-c("ID", "Site","Location", "Death_Cause", "Genetic_type", "Min_t", "Min_tplus1", "Max_t", "Max_tplus1", "Diameter_t", "Diameter_tplus1", "Height_t", "Height_tplus1", "Rep_t", "Rep_tplus1", "Surv_t", "Surv_tplus1", "Year")
```

## Investigate relationships among possible state variables 
```{r, investigate state variables}
predictors<-cbind(pooled$Min_t, pooled$Diameter_t, pooled$Height_t, pooled$Max_t)

# What is the correlation amongst the predictor variables? 
correlation<-cor(predictors[, 1:4], use="pairwise.complete.obs")
colnames(correlation)<-c("Min", "Diameter", "Height", "Max")
rownames(correlation)<-c("Min", "Diameter", "Height", "Max")

correlation<-round(correlation, 2)
print(correlation)
#Over the entire dataset, there is the lowest correlation between diameter and height

```

## Exclude outliers 

```{r, exclude outliers}
#Remove individual deaths that were sprayed or fire or grinding
restrict<-subset(pooled, is.na(Death_Cause))

#Remove outliers (very large diameters)
restrict2<-subset(restrict, Diameter_t<800)

#Remove an individual at Big Cypress that went from diameter 1.4 to diameter 108 back to diameter 2.1 
restrict2 <- subset(restrict2, restrict2$ID != 5)

#Questioning why we did this? does this lead to model-eviction? 
#Range of diameter: [0, 800]
0.9*max(restrict2$Diameter_t) #700
#Range of height:  [0, 800]
0.9*max(restrict2$Height_t, na.rm=T) #800
```

## Divide dataset into size domains (seedlings and larges)
```{r divide data}
seedlings<-subset(restrict2, restrict2$Diameter_t<1.6)
seedlings<-subset(seedlings, seedlings$Height_t<16)
larges<-subset(restrict2, restrict2$Diameter_t>1.6)
larges<-subset(larges, larges$Height_t>16)

x1seq_larges<-seq(1.6, 800, length.out=50)
x2seq_larges<-seq(16, 800, length.out=50)

x1seq_seedlings<-seq(0, 1.6, length.out=50)
x2seq_seedlings<-seq(0, 16, length.out=50)

grad_status<-rep(NA, length(seedlings$ID))
for (i in 1:length(seedlings$ID)) {
  if (is.na(seedlings$Diameter_tplus1[i])) {
    grad_status[i]<-NA
  }
  else if (is.na(seedlings$Height_tplus1[i])) {
    grad_status[i]<-NA
  }
  else if (seedlings$Diameter_tplus1[i]>1.6& seedlings$Height_tplus1[i]>16) { grad_status[i]<-1}
  else {grad_status[i]<-0}
}

seedlings<-cbind(seedlings, grad_status)

```
# Exploratory Statistics 
There are 1512 individuals 

Big Cypress | Cape Canaveral | Chekika | Fort Pierce | Punta Gorda | Wild Turkey
------------|----------------|---------|-------------|-------------|------------
308         | 226            | 460     | 166         | 175         | 177        

Eastern | Hybrid | Western 
--------|--------|--------
  626   | 534    | 352
  
```{r exploratory statistics}
summary(seedlings$Site)
summary(seedlings$Genetic_type)
summary(as.factor(seedlings$Year))
        
summary(larges$Site)
summary(larges$Genetic_type)
summary(as.factor(larges$Year))

```
The number of deaths (0) by biotype:
```{r deaths by biotype}
table(seedlings$Surv_tplus1, seedlings$Genetic_type)
table(larges$Surv_tplus1, larges$Genetic_type)
```
The number of deaths(0) by site:
```{r deaths by site}
table(seedlings$Surv_tplus1, seedlings$Site)
table(larges$Surv_tplus1, larges$Site)

```
```{r deaths by year}
table(seedlings$Surv_tplus1, seedlings$Year)
table(larges$Surv_tplus1, larges$Year)

```
# Define some plotting variables: 

```{r setup plotting}
x1seq_seedlings<-seq(0, 1.6, length.out=50)

x2seq_seedlings<-seq(0, 16, length.out=50)
x1seq_larges <- seq(0, 800, length.out = 50 )
x2seq_larges <- seq (0, 800, length.out = 50)

invlogit<-function(x){exp(x)/(1+exp(x))}

# Function to do an image plot of a matrix in the usual orientation, A(1,1) at top left  
matrix.image=function(x,y,A,col=topo.colors(200),...) {
	nx=length(x); ny=length(y); 
	x1=c(1.5*x[1]-0.5*x[2],1.5*x[nx]-0.5*x[nx-1]); 
	y1=c(1.5*y[1]-0.5*y[2],1.5*y[ny]-0.5*y[ny-1]); 
	image.plot(list(x=x,y=y,z=t(A)),xlim=x1,ylim=rev(y1),col=col,bty="u",...);  
}

```
# 1. D1 Growth
Choosing which state variables to use and whether to include terms for biotype, site or year
(for the year effect, only including data from years where all sites were sampled, so AIC cannot be compared with other models) 

* Diameter-only models: 
    * m1: logit(m) = b0 + b1(diameter)
    * m2: logit(m) = b0 + b1(diameter) + epsilon(biotype{E,H,W})
    * m3: logit(m) = b0 + b1(diameter) + epsilon(site{BC, CC, C, FP, PG, WT})
    * m4: logit(m) = b0 + b1(diameter) + epsilon(year{2010, 2011, 2012, 2013, 2014}
* Height-only models
    * m5: logit(m) = b0 + b1(height)
    * m6: logit(m) = b0 + b1(height) + epsilon(biotype{E,H,W})
    * m7: logit(m) = b0 + b1(height) + epsilon(site{BC, CC, C, FP, PG, WT})
    * m8: logit(m) = b0 + b1(height) + epsilon(year{2010, 2011, 2012, 2013, 2014}
* Diameter + Height models
    * m9: logit(m) = b0 + b1(diameter) + b2(height)
    * m10: logit(m) = b0 + b1(diameter) + b2(height) + epsilon(biotype{E,H,W})
    * m11: logit(m) = b0 + b1(diameter) + b2(height) + epsilon(site{BC, CC, C, FP, PG,WT})
    * m12: loigt(m) = b0 + b1(diameter) + b2(height) + epsilon(year{2010, 2011, 2012, 2013, 2014})

### -Diameter-only models

### -- g1_1: mu_x= b0 + b1(diameter) -----
```{r m1}
g1_1 <- lm(seedlings$Diameter_tplus1 ~ seedlings$Diameter_t)
summary(g1_1)
#Variance in Growth
sd_x <- summary(g1_1)$sigma


preds2 <- g1_1$coefficients[1] + g1_1$coefficients[2]*x1seq_seedlings + 2*sd_x
preds3 <- g1_1$coefficients[1] + g1_1$coefficients[2]*x1seq_seedlings - 2*sd_x
preds4 <- g1_1$coefficients[1] + g1_1$coefficients[2]*x1seq_seedlings + 1*sd_x
preds5 <- g1_1$coefficients[1] + g1_1$coefficients[2]*x1seq_seedlings - 1*sd_x



plot(x1seq_seedlings, g1_1$coeff[1] + g1_1$coeff[2]*x1seq_seedlings, type='l' , xlab = "Diameter at t (mm)", ylab="Diameter at t+1 (mm)")
polygon(c(rev(x1seq_seedlings), x1seq_seedlings), c(rev(preds3), preds2), col = 'grey90', border = NA)
polygon(c(rev(x1seq_seedlings), x1seq_seedlings), c(rev(preds5), preds4), col = 'grey80', border = NA)
points(seedlings$Diameter_t, seedlings$Diameter_tplus1)
abline(g1_1)


```

### --g1_2: mu_x = b0 + b1(diameter) + epsilon(biotype{E,H,W})
Hybrid is not significantly different from Eastern
```{r m2, fig.width=9, fig.height=4}

g1_2 <- lm(seedlings$Diameter_tplus1 ~ seedlings$Diameter_t + seedlings$Genetic_type)
summary(g1_2)
#Variance in Growth
sd_x <- summary(g1_2)$sigma

par(mfrow=c(1,2))
#Eastern/Hybrid
preds2 <- g1_2$coefficients[1] + g1_2$coefficients[2]*x1seq_seedlings  + 2*sd_x
preds3 <- g1_2$coefficients[1] + g1_2$coefficients[2]*x1seq_seedlings - 2*sd_x
preds4 <- g1_2$coefficients[1] + g1_2$coefficients[2]*x1seq_seedlings + 1*sd_x
preds5 <- g1_2$coefficients[1] + g1_2$coefficients[2]*x1seq_seedlings - 1*sd_x

plot(x1seq_seedlings, g1_2$coeff[1] + g1_2$coeff[2]*x1seq_seedlings, type='l' , xlab = "Diameter at t (mm)", ylab="Diameter at t+1 (mm)")
polygon(c(rev(x1seq_seedlings), x1seq_seedlings), c(rev(preds3), preds2), col = 'grey90', border = NA)
polygon(c(rev(x1seq_seedlings), x1seq_seedlings), c(rev(preds5), preds4), col = 'grey80', border = NA)
points(seedlings$Diameter_t[seedlings$Genetic_type == "eastern" | seedlings$Genetic_type == "hybrid"], seedlings$Diameter_tplus1[seedlings$Genetic_type == "eastern" | seedlings$Genetic_type == "hybrid"])
lines(x1seq_seedlings, g1_2$coeff[1] + g1_2$coeff[2]*x1seq_seedlings)

#Western
preds2 <- g1_2$coefficients[1] + g1_2$coefficients[2]*x1seq_seedlings + g1_2$coefficients[4]   + 2*sd_x
preds3 <- g1_2$coefficients[1] + g1_2$coefficients[2]*x1seq_seedlings +   
  g1_2$coefficients[4]- 2*sd_x
preds4 <- g1_2$coefficients[1] + g1_2$coefficients[2]*x1seq_seedlings + 
  g1_2$coefficients[4]+ 1*sd_x
preds5 <- g1_2$coefficients[1] + g1_2$coefficients[2]*x1seq_seedlings + 
  g1_2$coefficients[4]- 1*sd_x

plot(x1seq_seedlings, g1_2$coeff[1] + g1_2$coeff[2]*x1seq_seedlings + g1_2$coefficients[4], 
     type='l' , xlab = "Diameter at t (mm)", ylab="Diameter at t+1 (mm)")
polygon(c(rev(x1seq_seedlings), x1seq_seedlings), c(rev(preds3), preds2), col = 'grey90', 
        border = NA)
polygon(c(rev(x1seq_seedlings), x1seq_seedlings), c(rev(preds5), preds4), col = 'grey80', 
        border = NA)
points(seedlings$Diameter_t[seedlings$Genetic_type == "western"], seedlings$Diameter_tplus1[seedlings$Genetic_type == "western"])
lines(x1seq_seedlings, g1_2$coeff[1] + g1_2$coeff[2]*x1seq_seedlings + g1_2$coefficients[4])




 
```

### --g1_3: mu_x= b0 + b1(diameter) + epsilon(biotype{BC, CC, C, FP, PG, WT})

Big Cypress, Cape Canaveral and Chekika are not different 
```{r g1_3}
 
g1_3 <- lm(seedlings$Diameter_tplus1 ~ seedlings$Diameter_t + seedlings$Site)
summary(g1_3)
#Variance in Growth
sd_x <- summary(g1_3)$sigma

par(mfrow=c(2,2))
#Big Cypress, Cape Canaveral and Chekika 
preds2 <- g1_3$coefficients[1] + g1_3$coefficients[2]*x1seq_seedlings  + 2*sd_x
preds3 <- g1_3$coefficients[1] + g1_3$coefficients[2]*x1seq_seedlings - 2*sd_x
preds4 <- g1_3$coefficients[1] + g1_3$coefficients[2]*x1seq_seedlings + 1*sd_x
preds5 <- g1_3$coefficients[1] + g1_3$coefficients[2]*x1seq_seedlings - 1*sd_x

plot(x1seq_seedlings, g1_3$coeff[1] + g1_3$coeff[2]*x1seq_seedlings, type='l' , xlab = "Diameter at t (mm)", ylab="Diameter at t+1 (mm)", main = "BC, CC, C")
polygon(c(rev(x1seq_seedlings), x1seq_seedlings), c(rev(preds3), preds2), col = 'grey90', border = NA)
polygon(c(rev(x1seq_seedlings), x1seq_seedlings), c(rev(preds5), preds4), col = 'grey80', border = NA)
points(seedlings$Diameter_t[seedlings$Site == "Big Cypress" | seedlings$Site == "Cape Canaveral" | seedlings$Site == "Chekika"], seedlings$Diameter_tplus1[seedlings$Site == "Big Cypress" | seedlings$Site == "Cape Canaveral" | seedlings$Site == "Chekika"])
lines(x1seq_seedlings, g1_3$coeff[1] + g1_3$coeff[2]*x1seq_seedlings)

#Fort Pierce
preds2 <- g1_3$coefficients[1] + g1_3$coefficients[2]*x1seq_seedlings + 
  g1_3$coefficients[5]  + 2*sd_x
preds3 <- g1_3$coefficients[1] + g1_3$coefficients[2]*x1seq_seedlings +   
  g1_3$coefficients[5]- 2*sd_x
preds4 <- g1_3$coefficients[1] + g1_3$coefficients[2]*x1seq_seedlings + 
  g1_3$coefficients[5]+ 1*sd_x
preds5 <- g1_3$coefficients[1] + g1_3$coefficients[2]*x1seq_seedlings + 
  g1_3$coefficients[5]- 1*sd_x

plot(x1seq_seedlings, g1_3$coeff[1] + g1_3$coeff[2]*x1seq_seedlings + g1_3$coefficients[5], 
     type='l' , xlab = "Diameter at t (mm)", ylab="Diameter at t+1 (mm)", main = "FP")
polygon(c(rev(x1seq_seedlings), x1seq_seedlings), c(rev(preds3), preds2), col = 'grey90', 
        border = NA)
polygon(c(rev(x1seq_seedlings), x1seq_seedlings), c(rev(preds5), preds4), col = 'grey80', 
        border = NA)
points(seedlings$Diameter_t[seedlings$Site == "Fort Pierce"], seedlings$Diameter_tplus1[seedlings$Site == "Fort Pierce"])
lines(x1seq_seedlings, g1_3$coeff[1] + g1_3$coeff[2]*x1seq_seedlings + g1_3$coefficients[5])

#Punta Gorda
preds2 <- g1_3$coefficients[1] + g1_3$coefficients[2]*x1seq_seedlings + 
  g1_3$coefficients[6]   + 2*sd_x
preds3 <- g1_3$coefficients[1] + g1_3$coefficients[2]*x1seq_seedlings +   
  g1_3$coefficients[6]- 2*sd_x
preds4 <- g1_3$coefficients[1] + g1_3$coefficients[2]*x1seq_seedlings + 
  g1_3$coefficients[6]+ 1*sd_x
preds5 <- g1_3$coefficients[1] + g1_3$coefficients[2]*x1seq_seedlings + 
  g1_3$coefficients[6]- 1*sd_x

plot(x1seq_seedlings, g1_3$coeff[1] + g1_3$coeff[2]*x1seq_seedlings + g1_3$coefficients[6], 
     type='l' , xlab = "Diameter at t (mm)", ylab="Diameter at t+1 (mm)", main = "PG")
polygon(c(rev(x1seq_seedlings), x1seq_seedlings), c(rev(preds3), preds2), col = 'grey90', 
        border = NA)
polygon(c(rev(x1seq_seedlings), x1seq_seedlings), c(rev(preds5), preds4), col = 'grey80', 
        border = NA)
points(seedlings$Diameter_t[seedlings$Site == "Punta Gorda"], seedlings$Diameter_tplus1[seedlings$Site == "Punta Gorda"])
lines(x1seq_seedlings, g1_3$coeff[1] + g1_3$coeff[2]*x1seq_seedlings + g1_3$coefficients[6])

#Wild Turkey
preds2 <- g1_3$coefficients[1] + g1_3$coefficients[2]*x1seq_seedlings + 
  g1_3$coefficients[7]   + 2*sd_x
preds3 <- g1_3$coefficients[1] + g1_3$coefficients[2]*x1seq_seedlings +   
  g1_3$coefficients[7]- 2*sd_x
preds4 <- g1_3$coefficients[1] + g1_3$coefficients[2]*x1seq_seedlings + 
  g1_3$coefficients[7]+ 1*sd_x
preds5 <- g1_3$coefficients[1] + g1_3$coefficients[2]*x1seq_seedlings + 
  g1_3$coefficients[7]- 1*sd_x

plot(x1seq_seedlings, g1_3$coeff[1] + g1_3$coeff[2]*x1seq_seedlings + g1_3$coefficients[7], 
     type='l' , xlab = "Diameter at t (mm)", ylab="Diameter at t+1 (mm)", main = "WT")
polygon(c(rev(x1seq_seedlings), x1seq_seedlings), c(rev(preds3), preds2), col = 'grey90', 
        border = NA)
polygon(c(rev(x1seq_seedlings), x1seq_seedlings), c(rev(preds5), preds4), col = 'grey80', 
        border = NA)
points(seedlings$Diameter_t[seedlings$Site == "Wild Turkey"], seedlings$Diameter_tplus1[seedlings$Site == "Wild Turkey"])
lines(x1seq_seedlings, g1_3$coeff[1] + g1_3$coeff[2]*x1seq_seedlings + g1_3$coefficients[7])


```


### --g1_4: mu_x = b0 + b1(diameter) + epsilon(year{2010, 2011, 2012, 2013}
There is no difference in seedling growth among years. 
```{r g1_4} 
seedlings2 <- subset(seedlings, seedlings$Year > 2009 & seedlings$Year <2014)
seedlings2$Year <- as.factor(seedlings2$Year)
g1_4 <- lm(seedlings2$Diameter_tplus1 ~ seedlings2$Diameter_t + seedlings2$Year)
summary(g1_4)
#Variance in Growth
sd_x <- summary(g1_4)$sigma
  
  
  
 
```

### - Height-only models 
### --g1_5: mu_y = b0 + b1(height) 
```{r m5}
  g1_5 <- lm(seedlings$Height_tplus1 ~ seedlings$Height_t)
summary(g1_5)
#Variance in Growth
sd_x <- summary(g1_5)$sigma


preds2 <- g1_5$coefficients[1] + g1_5$coefficients[2]*x2seq_seedlings + 2*sd_x
preds3 <- g1_5$coefficients[1] + g1_5$coefficients[2]*x2seq_seedlings - 2*sd_x
preds4 <- g1_5$coefficients[1] + g1_5$coefficients[2]*x2seq_seedlings + 1*sd_x
preds5 <- g1_5$coefficients[1] + g1_5$coefficients[2]*x2seq_seedlings - 1*sd_x



plot(x2seq_seedlings, g1_5$coeff[1] + g1_5$coeff[2]*x2seq_seedlings, type='l' , xlab = "Height at t (cm)", ylab="Height at t+1 (cm)")
polygon(c(rev(x2seq_seedlings), x2seq_seedlings), c(rev(preds3), preds2), col = 'grey90', border = NA)
polygon(c(rev(x2seq_seedlings), x2seq_seedlings), c(rev(preds5), preds4), col = 'grey80', border = NA)
points(seedlings$Height_t, seedlings$Height_tplus1)
abline(g1_5)


```
### --g1_6: mu_y = b0 + b1(height) + epsilon(biotype{E,H,W})
Hybrid and Eastern are not different
```{r m6}
g1_6 <- lm(seedlings$Height_tplus1 ~ seedlings$Height_t + seedlings$Genetic_type)
summary(g1_6)
#Variance in Growth
sd_x <- summary(g1_6)$sigma

par(mfrow=c(1,2))
#Eastern/Hybrid
preds2 <- g1_6$coefficients[1] + g1_6$coefficients[2]*x2seq_seedlings  + 2*sd_x
preds3 <- g1_6$coefficients[1] + g1_6$coefficients[2]*x2seq_seedlings - 2*sd_x
preds4 <- g1_6$coefficients[1] + g1_6$coefficients[2]*x2seq_seedlings + 1*sd_x
preds5 <- g1_6$coefficients[1] + g1_6$coefficients[2]*x2seq_seedlings - 1*sd_x

plot(x2seq_seedlings, g1_6$coeff[1] + g1_6$coeff[2]*x2seq_seedlings, type='l' , xlab = "Height at t (cm)", ylab="Height at t+1 (cm)")
polygon(c(rev(x2seq_seedlings), x2seq_seedlings), c(rev(preds3), preds2), col = 'grey90', border = NA)
polygon(c(rev(x2seq_seedlings), x2seq_seedlings), c(rev(preds5), preds4), col = 'grey80', border = NA)
points(seedlings$Height_t[seedlings$Genetic_type == "eastern" | seedlings$Genetic_type == "hybrid"], seedlings$Height_tplus1[seedlings$Genetic_type == "eastern" | seedlings$Genetic_type == "hybrid"])
lines(x2seq_seedlings, g1_6$coeff[1] + g1_6$coeff[2]*x2seq_seedlings)

#Western
preds2 <- g1_6$coefficients[1] + g1_6$coefficients[2]*x2seq_seedlings + g1_6$coefficients[4]   + 2*sd_x
preds3 <- g1_6$coefficients[1] + g1_6$coefficients[2]*x2seq_seedlings +   
  g1_6$coefficients[4]- 2*sd_x
preds4 <- g1_6$coefficients[1] + g1_6$coefficients[2]*x2seq_seedlings + 
  g1_6$coefficients[4]+ 1*sd_x
preds5 <- g1_6$coefficients[1] + g1_6$coefficients[2]*x2seq_seedlings + 
  g1_6$coefficients[4]- 1*sd_x

plot(x2seq_seedlings, g1_6$coeff[1] + g1_6$coeff[2]*x2seq_seedlings + g1_6$coefficients[4], 
     type='l' , xlab = "Height at t (cm)", ylab="Height at t+1 (cm)")
polygon(c(rev(x2seq_seedlings), x2seq_seedlings), c(rev(preds3), preds2), col = 'grey90', 
        border = NA)
polygon(c(rev(x2seq_seedlings), x2seq_seedlings), c(rev(preds5), preds4), col = 'grey80', 
        border = NA)
points(seedlings$Height_t[seedlings$Genetic_type == "western"], seedlings$Height_tplus1[seedlings$Genetic_type == "western"])
lines(x2seq_seedlings, g1_6$coeff[1] + g1_6$coeff[2]*x2seq_seedlings + g1_6$coefficients[4])




```
### --g1_7: mu_y = b0 + b1(height) + epsilon(site{BC, CC, C, FP, PG, WT})
Wild Turkey is the only site distict from all the rest (but how much of it is just that Wild Turkey has a much smaller sample size than the other sites?)
```{r s7} 
 g1_7 <- lm(seedlings$Height_tplus1 ~ seedlings$Height_t + seedlings$Site)
summary(g1_7)
#Variance in Growth
sd_x <- summary(g1_7)$sigma

par(mfrow=c(1,2))
#All sites except Wild Turkey 
preds2 <- g1_7$coefficients[1] + g1_7$coefficients[2]*x2seq_seedlings  + 2*sd_x
preds3 <- g1_7$coefficients[1] + g1_7$coefficients[2]*x2seq_seedlings - 2*sd_x
preds4 <- g1_7$coefficients[1] + g1_7$coefficients[2]*x2seq_seedlings + 1*sd_x
preds5 <- g1_7$coefficients[1] + g1_7$coefficients[2]*x2seq_seedlings - 1*sd_x

plot(x2seq_seedlings, g1_7$coeff[1] + g1_7$coeff[2]*x2seq_seedlings, type='l' , xlab = "Height at t (mm)", ylab="Height at t+1 (mm)", main = "BC, CC, C, FP, PG")
polygon(c(rev(x2seq_seedlings), x2seq_seedlings), c(rev(preds3), preds2), col = 'grey90', border = NA)
polygon(c(rev(x2seq_seedlings), x2seq_seedlings), c(rev(preds5), preds4), col = 'grey80', border = NA)
points(seedlings$Height_t[seedlings$Site != "Wild Turkey"],
       seedlings$Height_tplus1[seedlings$Site != "Wild Turkey"])
lines(x2seq_seedlings, g1_7$coeff[1] + g1_7$coeff[2]*x2seq_seedlings)

plot(x2seq_seedlings, g1_7$coeff[1] + g1_7$coeff[2]*x2seq_seedlings +g1_7$coeff[7], type='l' , xlab = "Height at t (mm)", ylab="Height at t+1 (mm)", main = "WT")
polygon(c(rev(x2seq_seedlings), x2seq_seedlings), c(rev(preds3), preds2), col = 'grey90', border = NA)
polygon(c(rev(x2seq_seedlings), x2seq_seedlings), c(rev(preds5), preds4), col = 'grey80', border = NA)
points(seedlings$Height_t[seedlings$Site == "Wild Turkey"],
       seedlings$Height_tplus1[seedlings$Site == "Wild Turkey"])
lines(x2seq_seedlings, g1_7$coeff[1] + g1_7$coeff[2]*x2seq_seedlings + g1_7$coeff[7])
```
### --g1_8: mu_y = b0 + b1(height) + epsilon(year{2010, 2011, 2012, 2013}
2013 is different from the rest of the years, although once again it could just be the smaller sample size. 
```{r g1_8}
g1_8 <- lm(seedlings2$Height_tplus1 ~ seedlings2$Height_t + seedlings2$Year)
summary(g1_8)
#Variance in Growth
sd_x <- summary(g1_8)$sigma

preds2 <- g1_8$coefficients[1] + g1_8$coefficients[2]*x2seq_seedlings  + 2*sd_x
preds3 <- g1_8$coefficients[1] + g1_8$coefficients[2]*x2seq_seedlings - 2*sd_x
preds4 <- g1_8$coefficients[1] + g1_8$coefficients[2]*x2seq_seedlings + 1*sd_x
preds5 <- g1_8$coefficients[1] + g1_8$coefficients[2]*x2seq_seedlings - 1*sd_x

par(mfrow=c(1,2))
plot(x2seq_seedlings, g1_8$coeff[1] + g1_8$coeff[2]*x2seq_seedlings, type='l' , xlab = "Height at t (mm)", ylab="Height at t+1 (mm)", main = "2010, 2011, 2012")
polygon(c(rev(x2seq_seedlings), x2seq_seedlings), c(rev(preds3), preds2), col = 'grey90', border = NA)
polygon(c(rev(x2seq_seedlings), x2seq_seedlings), c(rev(preds5), preds4), col = 'grey80', border = NA)
points(seedlings2$Height_t[seedlings2$Year != "2013"],
       seedlings2$Height_tplus1[seedlings2$Year != "2013"])
lines(x2seq_seedlings, g1_8$coeff[1] + g1_8$coeff[2]*x2seq_seedlings)

preds2 <- g1_8$coefficients[1] + g1_8$coefficients[2]*x2seq_seedlings + g1_8$coeff[5]  + 2*sd_x
preds3 <- g1_8$coefficients[1] + g1_8$coefficients[2]*x2seq_seedlings+ g1_8$coeff[5] - 2*sd_x
preds4 <- g1_8$coefficients[1] + g1_8$coefficients[2]*x2seq_seedlings + g1_8$coeff[5]+ 1*sd_x
preds5 <- g1_8$coefficients[1] + g1_8$coefficients[2]*x2seq_seedlings + g1_8$coeff[5]- 1*sd_x
plot(x2seq_seedlings, g1_8$coeff[1] + g1_8$coeff[2]*x2seq_seedlings + g1_8$coeff[5], type='l' , xlab = "Height at t (mm)", ylab="Height at t+1 (mm)", main = "2013")
polygon(c(rev(x2seq_seedlings), x2seq_seedlings), c(rev(preds3), preds2), col = 'grey90', border = NA)
polygon(c(rev(x2seq_seedlings), x2seq_seedlings), c(rev(preds5), preds4), col = 'grey80', border = NA)
points(seedlings2$Height_t[seedlings2$Year == "2013"],
       seedlings2$Height_tplus1[seedlings2$Year == "2013"])
lines(x2seq_seedlings, g1_8$coeff[1] + g1_8$coeff[2]*x2seq_seedlings + g1_8$coeff[5])



```
### - Diameter + Height models 
### --g1_9: mu_x = b0 + b1(diameter) + b2(height)
#           mu_y = b3 + b4(diameter) + b5(height)
#These models are actually doing a terrible job of predicting future diameter and height!
#Which makes sense, because this model is supposed to be predicting growth of individuals that REMAIN in the seedling size domain and DO NOT recruit into the D2 size range. 
```{r s9}
  g1_9 <-manova(cbind(seedlings$Diameter_tplus1, seedlings$Height_tplus1) ~ seedlings$Diameter_t+seedlings$Height_t)
summary(g1_9)
sd_x<-summary(lm(seedlings$Diameter_tplus1 ~ seedlings$Diameter_t + seedlings$Height_t))$sigma

#Grab parameters associated with future diameter
b0<-g1_9$coeff[1,1]
b1<-g1_9$coeff[2,1]
b2<-g1_9$coeff[3,1]



#Grab parameters associated with future height
b3<-g1_9$coeff[1,2]
b4<-g1_9$coeff[2,2]
b5<-g1_9$coeff[3,2]
sd_y <-summary(lm(seedlings$Height_tplus1 ~ seedlings$Diameter_t + seedlings$Height_t))$sigma
 
 

z1<-outer(x1seq_seedlings, x2seq_seedlings, function(a,b) (invlogit(b0 + b1*a + b2*b)))
z2<- outer(x1seq_seedlings, x2seq_seedlings, function(a,b) (invlogit(b3+ b4*a + b5*b)))

par(mfrow=c(1,2))
pmat<-persp(x1seq_seedlings, x2seq_seedlings, z1, ticktype="detailed",
      theta=-30, zlim=c(0,4.1), zlab="\n Diameter at t+1 (mm)", 
      shade=0.1, nticks=4, xlab="\n Diameter at t(mm)", 
      ylab="\n Height at t(cm)",  lwd=1, xaxs="i", 
      main="", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(seedlings$Diameter_t, seedlings$Height_t, seedlings$Diameter_tplus1, pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)
#Now for future height:
pmat<-persp(x1seq_seedlings, x2seq_seedlings, z2, ticktype="detailed",
      theta=-30, zlim=c(0,44), zlab="\n Height at t+1 (mm)", 
      shade=0.1, nticks=4, xlab="\n Diameter at t(mm)", 
      ylab="\n Height at t(cm)",  lwd=1, xaxs="i", 
      main="", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(seedlings$Diameter_t, seedlings$Height_t, seedlings$Height_tplus1, pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)


par(mfrow=c(1,1))
par(mar=c(5.1,4.1,4.1,6))
coeff_bigger=1
image.plot(x1seq_seedlings, x2seq_seedlings, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", col=my.palette, legend.lab = "Diameter at t+1 (mm)")
points(seedlings$Diameter_t, seedlings$Height_t, cex=seedlings$Diameter_tplus1*coeff_bigger,  pch=1)
legend(0, 18.5, pch=1,text.width=0.1, pt.cex = c(0.5,1, 1.5, 2,2.5, 3, 3.5,4), c("0.5", "1", "1.5", "2", "2.5", "3", "3.5", "4"), xpd=T, horiz = T, title="Diameter at t +1 (mm)")
#text (seedlings$Diameter_t , seedlings$Height_t , seedlings$Diameter_tplus1 )


my.palette <- viridis(9)
par(mar=c(5.1,4.1,4.1,6))
coeff_bigger=0.1
image.plot(x1seq_seedlings, x2seq_seedlings, z2, xlab = "Diameter (mm) ", ylab="Height (cm)", col=alpha(my.palette, 0.2), legend.lab = "Height at t+1 (cm)")
points(seedlings$Diameter_t, seedlings$Height_t, cex=seedlings$Height_tplus1*coeff_bigger,  pch=1, col=my.palette, bg = "white")
legend(0, 18.5, pch=1,text.width=0.1, pt.cex = c(3,8, 13,18, 23, 28, 33, 38, 44)*coeff_bigger, c("3", "8", "13", "23", "28", "33", "38", "44"), xpd=T, horiz = T, title="Height at t +1 (cm)")
#text (seedlings$Diameter_t , seedlings$Height_t , seedlings$Diameter_tplus1 )

```
### --g1_10: mu_x = b0 + b1(diameter) + b2(height) + epsilon(biotype{E,H,W})
             mu_y = b3 + b4(diameter) + b5(height) + epsilon(biotype{E,H,W})

```{r g1_10}
g1_10 <-manova(cbind(seedlings$Diameter_tplus1, seedlings$Height_tplus1) ~ seedlings$Diameter_t+seedlings$Height_t + seedlings$Genetic_type)
summary(g1_10)
sd_x<-summary(lm(seedlings$Diameter_tplus1 ~ seedlings$Diameter_t + seedlings$Height_t + seedlings$Genetic_type))$sigma

##EASTERN
#Grab parameters associated with future diameter
b0<-g1_10$coeff[1,1]
b1<-g1_10$coeff[2,1]
b2<-g1_10$coeff[3,1]



#Grab parameters associated with future height
b3<-g1_10$coeff[1,2]
b4<-g1_10$coeff[2,2]
b5<-g1_10$coeff[3,2]
sd_y <-summary(lm(seedlings$Height_tplus1 ~ seedlings$Diameter_t + seedlings$Height_t + seedlings$Genetic_type))$sigma
 
 

z1<-outer(x1seq_seedlings, x2seq_seedlings, function(a,b) (invlogit(b0 + b1*a + b2*b )))
z2<- outer(x1seq_seedlings, x2seq_seedlings, function(a,b) (invlogit(b3+ b4*a + b5*b)))

par(mfrow=c(1,2))
pmat<-persp(x1seq_seedlings, x2seq_seedlings, z1, ticktype="detailed",
      theta=-30, zlim=c(0,4.1), zlab="\n Diameter at t+1 (mm)", 
      shade=0.1, nticks=4, xlab="\n Diameter at t(mm)", 
      ylab="\n Height at t(cm)",  lwd=1, xaxs="i", 
      main="Eastern", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(seedlings$Diameter_t[seedlings$Genetic_type == "eastern"], seedlings$Height_t[seedlings$Genetic_type == "eastern"], seedlings$Diameter_tplus1[seedlings$Genetic_type == "eastern"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)


#Now for future height:
pmat<-persp(x1seq_seedlings, x2seq_seedlings, z2, ticktype="detailed",
      theta=-30, zlim=c(0,44), zlab="\n Height at t+1 (mm)", 
      shade=0.1, nticks=4, xlab="\n Diameter at t(mm)", 
      ylab="\n Height at t(cm)",  lwd=1, xaxs="i", 
      main="Eastern", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(seedlings$Diameter_t[seedlings$Genetic_type == "eastern"], seedlings$Height_t[seedlings$Genetic_type == "eastern"], seedlings$Height_tplus1[seedlings$Genetic_type =="eastern"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)


par(mfrow=c(2,1))
par(mar=c(5.1,4.1,4.1,6))
coeff_bigger=1
image.plot(x1seq_seedlings, x2seq_seedlings, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", col=my.palette, legend.lab = "Diameter at t+1 (mm)")
points(seedlings$Diameter_t[seedlings$Genetic_type == "eastern"], seedlings$Height_t[seedlings$Genetic_type == "hybrid"], cex=seedlings$Diameter_tplus1[seedlings$Genetic_type == "hybrid"]*coeff_bigger,  pch=1)
legend(0, 18.5, pch=1,text.width=0.1, pt.cex = c(0.5,1, 1.5, 2,2.5, 3, 3.5,4), c("0.5", "1", "1.5", "2", "2.5", "3", "3.5", "4"), xpd=T, horiz = T, title="Diameter at t +1 (mm)")
#text (seedlings$Diameter_t , seedlings$Height_t , seedlings$Diameter_tplus1 )


my.palette <- viridis(9)
par(mar=c(5.1,4.1,4.1,6))
coeff_bigger=0.1
image.plot(x1seq_seedlings, x2seq_seedlings, z2, xlab = "Diameter (mm) ", ylab="Height (cm)", col=my.palette, main ="Eastern",legend.lab = "Height at t+1 (cm)")
points(seedlings$Diameter_t[seedlings$Genetic_type == "eastern"], seedlings$Height_t[seedlings$Genetic_type == "eastern"], cex=seedlings$Height_tplus1[seedlings$Genetic_type == "eastern"]*coeff_bigger,  pch=1, bg = "white")
legend(0, 18.5, pch=1,text.width=0.1, pt.cex = c(3,8, 13,18, 23, 28, 33, 38, 44)*coeff_bigger,c("3", "8", "13", "23", "28", "33", "38", "44"), xpd=T, horiz = T, title="Height at t +1 (cm)")
#text (seedlings$Diameter_t , seedlings$Height_t , seedlings$Diameter_tplus1 )


##Hybrid
#Grab parameters associated with future diameter
b0<-g1_10$coeff[1,1] + g1_10$coeff[4,1]
b1<-g1_10$coeff[2,1]
b2<-g1_10$coeff[3,1]



#Grab parameters associated with future height
b3<-g1_10$coeff[1,2] + g1_10$coeff[4,2]
b4<-g1_10$coeff[2,2]
b5<-g1_10$coeff[3,2]
sd_y <-summary(lm(seedlings$Height_tplus1 ~ seedlings$Diameter_t + seedlings$Height_t + seedlings$Genetic_type))$sigma
 
 

z1<-outer(x1seq_seedlings, x2seq_seedlings, function(a,b) (invlogit(b0 + b1*a + b2*b )))
z2<- outer(x1seq_seedlings, x2seq_seedlings, function(a,b) (invlogit(b3+ b4*a + b5*b)))

par(mfrow=c(1,2))
pmat<-persp(x1seq_seedlings, x2seq_seedlings, z1, ticktype="detailed",
      theta=-30, zlim=c(0,4.1), zlab="\n Diameter at t+1 (mm)", 
      shade=0.1, nticks=4, xlab="\n Diameter at t(mm)", 
      ylab="\n Height at t(cm)",  lwd=1, xaxs="i", 
      main="Hybrid", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(seedlings$Diameter_t[seedlings$Genetic_type == "hybrid"], seedlings$Height_t[seedlings$Genetic_type == "hybrid"], seedlings$Diameter_tplus1[seedlings$Genetic_type == "hybrid"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)


#Now for future height:
pmat<-persp(x1seq_seedlings, x2seq_seedlings, z2, ticktype="detailed",
      theta=-30, zlim=c(0,44), zlab="\n Height at t+1 (mm)", 
      shade=0.1, nticks=4, xlab="\n Diameter at t(mm)", 
      ylab="\n Height at t(cm)",  lwd=1, xaxs="i", 
      main="Hybrid", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(seedlings$Diameter_t[seedlings$Genetic_type == "hybrid"], seedlings$Height_t[seedlings$Genetic_type == "hybrid"], seedlings$Height_tplus1[seedlings$Genetic_type =="hybrid"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)


par(mfrow=c(2,1))
par(mar=c(5.1,4.1,4.1,6))
coeff_bigger=1
image.plot(x1seq_seedlings, x2seq_seedlings, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", col=my.palette, legend.lab = "Diameter at t+1 (mm)")
points(seedlings$Diameter_t[seedlings$Genetic_type == "hybrid"], seedlings$Height_t[seedlings$Genetic_type == "hybrid"], cex=seedlings$Diameter_tplus1[seedlings$Genetic_type == "hybrid"]*coeff_bigger,  pch=1)
legend(0, 18.5, pch=1,text.width=0.1, pt.cex = c(0.5,1, 1.5, 2,2.5, 3, 3.5,4), c("0.5", "1", "1.5", "2", "2.5", "3", "3.5", "4"), xpd=T, horiz = T, title="Diameter at t +1 (mm)")
#text (seedlings$Diameter_t , seedlings$Height_t , seedlings$Diameter_tplus1 )


my.palette <- viridis(9)
par(mar=c(5.1,4.1,4.1,6))
coeff_bigger=0.1
image.plot(x1seq_seedlings, x2seq_seedlings, z2, xlab = "Diameter (mm) ", ylab="Height (cm)", col=my.palette, main ="Hybrid",legend.lab = "Height at t+1 (cm)")
points(seedlings$Diameter_t[seedlings$Genetic_type == "hybrid"], seedlings$Height_t[seedlings$Genetic_type == "hybrid"], cex=seedlings$Height_tplus1[seedlings$Genetic_type == "hybrid"]*coeff_bigger,  pch=1, bg = "white")
legend(0, 18.5, pch=1,text.width=0.1, pt.cex = c(3,8, 13,18, 23, 28, 33, 38, 44)*coeff_bigger,c("3", "8", "13", "23", "28", "33", "38", "44"), xpd=T, horiz = T, title="Height at t +1 (cm)")
#text (seedlings$Diameter_t , seedlings$Height_t , seedlings$Diameter_tplus1 )


```
### --m11: logit(m) = b0 + b1(diameter) + b2(height) + epsilon(site{BC, CC, C, FP, PG,WT})

Big Cypress, Cape Canaveral, Fort Pierce and Punta Gorda are not different 
```{r m11}
m11 <- glm(seedlings$grad_status ~ seedlings$Diameter_t + seedlings$Height_t + 
              seedlings$Site, family = binomial)
summary(m11)
 
par(mfrow=c(1,3)) 
  #Big Cypress, Cape Canaveral, Fort Pierce and Punta Gorda 
b0 <- m11$coeff[1]
b1 <- m11$coeff[2]
b2 <- m11$coeff[3]
z1<-outer(x1seq_seedlings, x2seq_seedlings, function(a,b) (invlogit(b0 + b1*a + b2*b)))

pmat<-persp(x1seq_seedlings, x2seq_seedlings, z1, ticktype="detailed",
      theta=-30, zlim=c(0, 1.25), zlab="\n P(Maturation)", 
      shade=0.1, nticks=4, xlab="\n Diameter (mm)", 
      ylab="\n Height (cm)",  lwd=1, xaxs="i", 
      main="BC, CC, FP, PG", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(seedlings$Diameter_t[seedlings$Site=="Big Cypress" | seedlings$Site == "Cape Canaveral" | seedlings$Site == "Fort Pierce" | seedlings$Site == "Punta Gorda"], seedlings$Height_t[seedlings$Site=="Big Cypress" | seedlings$Site == "Cape Canaveral" | seedlings$Site == "Fort Pierce" | seedlings$Site == "Punta Gorda"], seedlings$grad_status[seedlings$Site=="Big Cypress" | seedlings$Site == "Cape Canaveral" | seedlings$Site == "Fort Pierce" | seedlings$Site == "Punta Gorda"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)

#Chekika
b0 <- m11$coeff[1] + m11$coeff[5]
b1 <- m11$coeff[2] 
b2 <- m11$coeff[3]
z1<-outer(x1seq_seedlings, x2seq_seedlings, function(a,b) (invlogit(b0 + b1*a + b2*b)))

pmat<-persp(x1seq_seedlings, x2seq_seedlings, z1, ticktype="detailed",
      theta=-30, zlim=c(0, 1.25), zlab="\n P(Maturation)", 
      shade=0.1, nticks=4, xlab="\n Diameter (mm)", 
      ylab="\n Height (cm)",  lwd=1, xaxs="i", 
      main="C", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(seedlings$Diameter_t[seedlings$Site=="Chekika"], seedlings$Height_t[seedlings$Site=="Chekika"], seedlings$grad_status[seedlings$Site=="Chekika"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)


#Wild Turkey
b0 <- m11$coeff[1] + m11$coeff[8]
b1 <- m11$coeff[2] 
b2 <- m11$coeff[3]
z1<-outer(x1seq_seedlings, x2seq_seedlings, function(a,b) (invlogit(b0 + b1*a + b2*b)))

pmat<-persp(x1seq_seedlings, x2seq_seedlings, z1, ticktype="detailed",
      theta=-30, zlim=c(0, 1.25), zlab="\n P(Maturation)", 
      shade=0.1, nticks=4, xlab="\n Diameter (mm)", 
      ylab="\n Height (cm)",  lwd=1, xaxs="i", 
      main="WT", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(seedlings$Diameter_t[seedlings$Site=="Wild Turkey"], seedlings$Height_t[seedlings$Site=="Wild Turkey"], seedlings$grad_status[seedlings$Site=="Wild Turkey"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)


####### Image plots 

par(mfrow=c(1,3)) 
#Big Cypress, Cape Canaveral, Fort Pierce and Punta Gorda 
b0 <- m11$coeff[1]
b1 <- m11$coeff[2]
b2 <- m11$coeff[3]
z1<-outer(x1seq_seedlings, x2seq_seedlings, function(a,b) (invlogit(b0 + b1*a + b2*b)))

image.plot(x1seq_seedlings, x2seq_seedlings, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="BC, CC, FP, PG", col=my.palette)
points(seedlings$Diameter_t[seedlings$grad_status==1 & (seedlings$Site=="Big Cypress" | seedlings$Site == "Cape Canaveral" | seedlings$Site == "Fort Pierce" | seedlings$Site == "Punta Gorda")], seedlings$Height_t[seedlings$grad_status==1& (seedlings$Site=="Big Cypress" | seedlings$Site == "Cape Canaveral" | seedlings$Site == "Fort Pierce" | seedlings$Site == "Punta Gorda")], pch=19)
points(seedlings$Diameter_t[seedlings$grad_status==0 & (seedlings$Site=="Big Cypress" | seedlings$Site == "Cape Canaveral" | seedlings$Site == "Fort Pierce" | seedlings$Site == "Punta Gorda")], seedlings$Height_t[seedlings$grad_status==0&(seedlings$Site=="Big Cypress" | seedlings$Site == "Cape Canaveral" | seedlings$Site == "Fort Pierce" | seedlings$Site == "Punta Gorda")], pch=1)
legend(1.63, 15, pch=c(1,19), cex = 0.8, text.width=0.19, c("Seedling at t+1", "Adult at t+1"), xpd=T)


#Chekika
b0 <- m11$coeff[1] + m11$coeff[5]
b1 <- m11$coeff[2] 
b2 <- m11$coeff[3]
z1<-outer(x1seq_seedlings, x2seq_seedlings, function(a,b) (invlogit(b0 + b1*a + b2*b)))

image.plot(x1seq_seedlings, x2seq_seedlings, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="C", col=my.palette)
points(seedlings$Diameter_t[seedlings$grad_status==1 & seedlings$Site=="Chekika"], seedlings$Height_t[seedlings$grad_status==1& seedlings$Site=="Chekika"], pch=19)
points(seedlings$Diameter_t[seedlings$grad_status==0 & seedlings$Site=="Chekika"], seedlings$Height_t[seedlings$grad_status==0&seedlings$Site=="Chekika"], pch=1)
legend(1.63, 15, pch=c(1,19), cex = 0.8, text.width=0.19, c("Seedling at t+1", "Adult at t+1"), xpd=T)

#Wild Turkey
b0 <- m11$coeff[1] + m11$coeff[8]
b1 <- m11$coeff[2] 
b2 <- m11$coeff[3]
z1<-outer(x1seq_seedlings, x2seq_seedlings, function(a,b) (invlogit(b0 + b1*a + b2*b)))

image.plot(x1seq_seedlings, x2seq_seedlings, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="WT", col=my.palette)
points(seedlings$Diameter_t[seedlings$grad_status==1 & seedlings$Site=="Wild Turkey"], seedlings$Height_t[seedlings$grad_status==1& seedlings$Site=="Wild Turkey"], pch=19)
points(seedlings$Diameter_t[seedlings$grad_status==0 & seedlings$Site=="Wild Turkey"], seedlings$Height_t[seedlings$grad_status==0&seedlings$Site=="Wild Turkey"], pch=1)
legend(1.63, 15, pch=c(1,19), cex = 0.8, text.width=0.19, c("Seedling at t+1", "Adult at t+1"), xpd=T)


```
### --m12: logit(m) = b0 + b1(diameter) + b2(height) + epsilon(year{2010, 2011, 2012, 2013, 2014})
2010 and 2011 are not different 
```{r m12}
m12 <- glm(seedlings2$grad_status ~ seedlings2$Diameter_t + seedlings2$Height_t + 
              seedlings2$Year, family = binomial)
summary(m12)
 
par(mfrow=c(2,2)) 
#2010
b0 <- m12$coeff[1]
b1 <- m12$coeff[2]
b2 <- m12$coeff[3]
z1<-outer(x1seq_seedlings, x2seq_seedlings, function(a,b) (invlogit(b0 + b1*a + b2*b)))

pmat<-persp(x1seq_seedlings, x2seq_seedlings, z1, ticktype="detailed",
      theta=-30, zlim=c(0, 1.25), zlab="\n P(Maturation)", 
      shade=0.1, nticks=4, xlab="\n Diameter (mm)", 
      ylab="\n Height (cm)",  lwd=1, xaxs="i", 
      main="2010, 2011", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(seedlings$Diameter_t[seedlings2$Year=="2010" |seedlings2$Year=="2011"], seedlings$Height_t[seedlings2$Year =="2010" | seedlings2$Year == "2011"], seedlings$grad_status[seedlings2$Year=="2010" | seedlings2$Year == "2011"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)

#2012
b0 <- m12$coeff[1] + m12$coeff[5]
b1 <- m12$coeff[2]
b2 <- m12$coeff[3]
z1<-outer(x1seq_seedlings, x2seq_seedlings, function(a,b) (invlogit(b0 + b1*a + b2*b)))

pmat<-persp(x1seq_seedlings, x2seq_seedlings, z1, ticktype="detailed",
      theta=-30, zlim=c(0, 1.25), zlab="\n P(Maturation)", 
      shade=0.1, nticks=4, xlab="\n Diameter (mm)", 
      ylab="\n Height (cm)",  lwd=1, xaxs="i", 
      main="2011", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(seedlings$Diameter_t[seedlings2$Year=="2012"], seedlings$Height_t[seedlings2$Year =="2012"], seedlings$grad_status[seedlings2$Year=="2012"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)

#2013
b0 <- m12$coeff[1] + m12$coeff[6]
b1 <- m12$coeff[2]
b2 <- m12$coeff[3]
z1<-outer(x1seq_seedlings, x2seq_seedlings, function(a,b) (invlogit(b0 + b1*a + b2*b)))

pmat<-persp(x1seq_seedlings, x2seq_seedlings, z1, ticktype="detailed",
      theta=-30, zlim=c(0, 1.25), zlab="\n P(Maturation)", 
      shade=0.1, nticks=4, xlab="\n Diameter (mm)", 
      ylab="\n Height (cm)",  lwd=1, xaxs="i", 
      main="2013", cex.main=1)

# from 3D to 2D coordinates
mypoints <- trans3d(seedlings$Diameter_t[seedlings2$Year=="2013"], seedlings$Height_t[seedlings2$Year =="2013"], seedlings$grad_status[seedlings2$Year=="2013"], pmat=pmat)
# plot in 2D space with pointsize related to distance
points(mypoints, col=4)

####### Image Plots 
par(mfrow=c(2,2))
#2010, 2011
b0 <- m12$coeff[1] 
b1 <- m12$coeff[2] 
b2 <- m12$coeff[3]
z1<-outer(x1seq_seedlings, x2seq_seedlings, function(a,b) (invlogit(b0 + b1*a + b2*b)))

image.plot(x1seq_seedlings, x2seq_seedlings, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="2010, 2011", col=my.palette)
points(seedlings2$Diameter_t[seedlings2$grad_status==1 & (seedlings2$Year=="2010" | seedlings2$Year == "2011")], seedlings2$Height_t[seedlings2$grad_status==1& (seedlings2$Year=="2010" | seedlings2$Year == "2011")], pch=19)
points(seedlings2$Diameter_t[seedlings2$grad_status==0 & (seedlings2$Year=="2010" | seedlings2$Year == "2011")], seedlings2$Height_t[seedlings2$grad_status==0&(seedlings2$Year=="2010" | seedlings2$Year == "2011")], pch=1)
legend(1.63, 15, pch=c(1,19), cex = 0.8, text.width=0.19, c("Seedling at t+1", "Adult at t+1"), xpd=T)



#2012
b0 <- m12$coeff[1] +m12$coeff[5]
b1 <- m12$coeff[2] 
b2 <- m12$coeff[3]
z1<-outer(x1seq_seedlings, x2seq_seedlings, function(a,b) (invlogit(b0 + b1*a + b2*b)))

image.plot(x1seq_seedlings, x2seq_seedlings, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="2012", col=my.palette)
points(seedlings2$Diameter_t[seedlings2$grad_status==1 & seedlings2$Year=="2012"], seedlings2$Height_t[seedlings2$grad_status==1& seedlings2$Year=="2012"], pch=19)
points(seedlings2$Diameter_t[seedlings2$grad_status==0 & seedlings2$Year=="2012"], seedlings2$Height_t[seedlings2$grad_status==0&seedlings2$Year=="2012"], pch=1)
legend(1.63, 15, pch=c(1,19), cex = 0.8, text.width=0.19, c("Seedling at t+1", "Adult at t+1"), xpd=T)


#2013
b0 <- m12$coeff[1] + m12$coeff[6]
b1 <- m12$coeff[2] 
b2 <- m12$coeff[3]
z1<-outer(x1seq_seedlings, x2seq_seedlings, function(a,b) (invlogit(b0 + b1*a + b2*b)))

image.plot(x1seq_seedlings, x2seq_seedlings, z1, xlab = "Diameter (mm) ", ylab="Height (cm)", main="2013", col=my.palette)
points(seedlings2$Diameter_t[seedlings2$grad_status==1 & seedlings2$Year=="2013"], seedlings2$Height_t[seedlings2$grad_status==1& seedlings2$Year=="2013"], pch=19)
points(seedlings2$Diameter_t[seedlings2$grad_status==0 & seedlings2$Year=="2013"], seedlings2$Height_t[seedlings2$grad_status==0&seedlings2$Year=="2013"], pch=1)
legend(1.63, 15, pch=c(1,19), cex = 0.8, text.width=0.19, c("Seedling at t+1", "Adult at t+1"), xpd=T)
```






















###- AIC
```{r seedling survival aic}
#For all models except year
aictab(list(m1, m2, m3, m5, m6, m7, m9, m10, m11), modnames= c("m1", "m2", "m3", "m5", 
                                                             "m6", "m7", "m9", "m10", "m11"))

#For comparing among the models with year: 
aictab(list(m4, m8, m12), modnames=c("m4", "m8", "m12"))

```


